### 2014-03-01 authorinstr_2.tex

\documentclass{article}
\usepackage{a4wide}

%% if your are not using LaTeX2e use instead
%% \documentstyle[bnaic]{article}

%% begin document with title, author and affiliations

\title{Seminarium IN3130\\ Title goes here}
\author{A. Hambenne  \and
    O. Maas \and
    R. Oosterloo}
\date{}

\pagestyle{empty}

\begin{document}
\maketitle
\thispagestyle{empty}

\begin{abstract}
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
This is the abstract of my paper.
\end{abstract}

\section{Introduction}

\section{Data}

\subsection{Twitter API}

\section{Single tweet analysis}
\subsection{Data enrichment}
\subsection{Sentiment analysis}
\subsection{Concept extraction}
\subsection{Metadata analysis (opt)}

\section{Tweet stream analysis}
\subsection{Statistics}
\subsection{user modeling}
\subsection{Classification}
\subsection{Tag based analysis}
\subsection{Event identification}

\section{Conclusion}

\bibliographystyle{plain}
\bibliography{mybibfile}

\end{document}

### 2014-03-01 authorinstr_2.tex
Bibtex gefixed
Eerste stukje geschreven, nog niet af

@@
 \usepackage{a4wide}
+\usepackage{cite}
 
@@
 \subsection{Event identification}
+\subsubsection{What is Event Identification}
+Event identification is the problem of identifying events(e.g.
+concerts, festivals \& incidents) in a twitter-stream.
+The events identified range from Worldwide to local events.
+Twitter-messages related to an event can be a useful source of information spreading information earlier than 'old' media.
 
+To identify an event, a definition of an event is needed.
+\cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
+occurrence and published during time $T_e$."
+
+\subsubsection{Event Identification Issues}
+
+\textbf{Aligning Tweets with an Event} \\
+On average thousands of tweets are sent using Twitter every minute. One of the main challenges in Event Identification is the alignment of tweets with their respective event. 
+\\\\
+\textbf{Separation of Event and Non-event Content}\\
+Because not all tweets on twitter are event content, a seperation of Event and Non-event content is done prior of identifying events.
+To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA).
+ICA doesn't require an number of clusters before the execution of the algorithm.
+This is an useful feature in the constantly changing twitter-environment.
+
+After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
+\begin{itemize}
+  \item Temporal: TODO
+  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
+  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
+  \item Twitter-centric: TODO
+\end{itemize}
+With this list of features a two event classifier is trained using two different techniques.
+The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used.
+According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.
 \section{Conclusion}
@@
 \bibliographystyle{plain}
-\bibliography{mybibfile}
+\bibliography{bibdb}
 

### 2014-03-01 authorinstr_2.tex
Aanpassingen volgorde en kleine verbeteringen

@@
 The events identified range from Worldwide to local events.
-Twitter-messages related to an event can be a useful source of information spreading information earlier than 'old' media.
+Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)
 
-To identify an event, a definition of an event is needed.
+To identify an event using an algorithm, a definition of an event is needed.
 \cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
@@
 \subsubsection{Event Identification Issues}
-
-\textbf{Aligning Tweets with an Event} \\
-On average thousands of tweets are sent using Twitter every minute. One of the main challenges in Event Identification is the alignment of tweets with their respective event. 
+In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
 \\\\ 
@@
 \end{itemize}
-With this list of features a two event classifier is trained using two different techniques.
+With this list of features two event-classifiers are trained using two different techniques.
 The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used.
 According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.
+\\\\
+\textbf{Aligning Tweets with an Event} \\
+On average thousands of tweets are sent using Twitter(bron) every minute.
+One of the main challenges in Event Identification is the alignment of tweets with their respective event.
+\cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
+
 \section{Conclusion}

### 2014-03-01 authorinstr_2.tex
Laatste aanpassingen voor vandaag. Vakcode aangepast, werktitel toegevoegd en een klein stukje geschreven

@@
 
-\title{Seminarium IN3130\\ Title goes here}
+\title{Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)}
 \author{A. Hambenne  \and
@@
 \textbf{Aligning Tweets with an Event} \\
-On average thousands of tweets are sent using Twitter(bron) every minute.
+On average thousands of tweets are sent every minute using Twitter(bron) .
 One of the main challenges in Event Identification is the alignment of tweets with their respective event.
 \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
-
+Twitter exposes the data using different formats such as JSON \& XML.
+To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable.
+The full enrichment process is described in section 2 of \cite{eventalign}.
+TODO
 \section{Conclusion}

### 2014-03-02 authorinstr_2.tex
Earthquake detection toegevoegd. Event alignment aangepast. Alles nog WIP

@@
 \subsection{Event identification}
-\subsubsection{What is Event Identification}
+
 Event identification is the problem of identifying events(e.g.
@@
 \begin{itemize}
-  \item Temporal: TODO
+	%TODO Temporal en Twittercentric uitwerken.
+  \item Temporal:
   \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
   \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
-  \item Twitter-centric: TODO
+  \item Twitter-centric: 
 \end{itemize}
+%TODO Weka toolkit uitzoeken
 With this list of features two event-classifiers are trained using two different techniques.
-The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used.
+The first classifier is trained using the "WEKA tookit", in the second classifier the  Naive-Bayes technique is used.
 According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.
@@
 \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
-Twitter exposes the data using different formats such as JSON \& XML.
+
+At first the data is enriched, Twitter exposes the data using different formats such as JSON \& XML.
 To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable.
 The full enrichment process is described in section 2 of \cite{eventalign}.
-TODO
+
+%TODO misschien wat meer info over het semantic web toevoegen.
+After this process \cite{eventalign} uses multiple techniques to align a tweet with the respective event.
+The first technique used by \cite{eventalign} is Feature Extraction.
+Three featuresets are used:
+\begin{itemize}
+%TODO uitwerken
+  \item Immediate Resource Leaves: TODO
+  \item 1-Step Resource Leaves 
+  \item DBPedia Concepts 
+\end{itemize}
+%TODO afmaken
+
+\subsubsection{Usecase: Earthquake Detection}
+In \cite{earthq} a usecase for Event Identification is presented in the form of a earthquake detection system.
+\cite{earthq} considers twitter users as sensors.
+If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.
+
+To distinguish between tweets about Earthquakes a number of features is used.
+(1) The number of words in a tweet (2) The words in a tweet (3) Word context features.
+Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users.
+
+With the above feature set as basis, a system that detects earthquakes using twitter was built.
+After the system detects an earthquake an email to all users is sent.
+The system was used during 18.
+august - 2 September.
+In this time period 10 earthquakes had occurred, all of these earthquakes were detected.
+Furthermore \cite{earthq}'s system detects an earthquake 10 minutes after happening and sends a message within a minute after detection.
 \section{Conclusion}

### 2014-03-03 authorinstr_2.tex
B
first bit about data enrichment

--- 2014-03-01 authorinstr_2.tex
@@
 \usepackage{a4wide}
-\usepackage{cite}
 
@@
 \section{Single tweet analysis}
+In this section we will discuss the different types of analysis that can be done on one single tweet.
+This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets.
 \subsection{Data enrichment}
+At the very basis of a tweet is data enrichment.
+Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about.
+To get a better understanding of the meaning of a tweet, a context is needed.
+For humans this is done by linking the information from the tweet to earlier acquired knowledge.\\
+Some tweets contain an URL, this makes it possible for a computer to create a context from the linked resource. This works 
 \subsection{Sentiment analysis}
@@
 \subsection{Event identification}
-\subsubsection{What is Event Identification}
-Event identification is the problem of identifying events(e.g.
-concerts, festivals \& incidents) in a twitter-stream.
-The events identified range from Worldwide to local events.
-Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)
-
-To identify an event using an algorithm, a definition of an event is needed.
-\cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
-occurrence and published during time $T_e$."
-
-\subsubsection{Event Identification Issues}
-In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
-\\\\ 
-\textbf{Separation of Event and Non-event Content}\\
-Because not all tweets on twitter are event content, a seperation of Event and Non-event content is done prior of identifying events.
-To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA).
-ICA doesn't require an number of clusters before the execution of the algorithm.
-This is an useful feature in the constantly changing twitter-environment.
-
-After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
-\begin{itemize}
-  \item Temporal: TODO
-  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
-  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
-  \item Twitter-centric: TODO
-\end{itemize}
-With this list of features two event-classifiers are trained using two different techniques.
-The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used.
-According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.
-\\\\
-\textbf{Aligning Tweets with an Event} \\
-On average thousands of tweets are sent using Twitter(bron) every minute.
-One of the main challenges in Event Identification is the alignment of tweets with their respective event.
-\cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
 
@@
 \bibliographystyle{plain}
-\bibliography{bibdb}
+\bibliography{mybibfile}
 

### 2014-03-03 authorinstr_2.tex

--- 2014-03-02 authorinstr_2.tex
@@
 \subsection{Statistics}
-\subsection{user modeling}
-\subsection{Classification}
+\subsection{User Modelling}
+\subsection{User Classification}
+
 \subsection{Tag based analysis}

### 2014-03-03 authorinstr_2.tex
Data enrichment

@@
 \subsection{Twitter API}
-
 \section{Single tweet analysis}
@@
 To get a better understanding of the meaning of a tweet, a context is needed.
-For humans this is done by linking the information from the tweet to earlier acquired knowledge.\\
-Some tweets contain an URL, this makes it possible for a computer to create a context from the linked resource. This works 
+For humans this is done by linking the information from the tweet to earlier acquired knowledge.
+\subsubsection{Data enrichment issues}
+The problem of linking tweets to another source of information poses the biggest issue in data enrichment.
+The tweets themselves do not provide much information.
+Fortunately, Kwak et al.
+have shown that the topic of over 85\% of the of the tweet is related to news \cite{newsmedia}.
+This knowledge can be leveraged to create a context for most of the tweets.
+This is what what Abel et al.
+proposed to do\cite{enrichmentForProfiling}.
+They linked tweets to mainstream news networks like CNN, BBC and New York Times.
+\\
+Linking to just news articles narrows the problem significantly, however, actually linking the tweets and the new articles still is an issue.
+Abel et al.
+propose two main linking strategies, divided into five methods total.
+\begin{enumerate}
+\item \textbf{URL-based strategy}\\
+This strategy is based upon the observation that many tweets contains URLs. Usually these URLs refer to news articles the tweets are closely related to.
+	\subitem \textbf{Strict URL-based} defines an article and a tweet as related when the tweet contains an URL to that news article.
+	\subitem \textbf{Lenient URL-based}, this method is an extension of the strict URL-based method.
+This extension entails that if a tweet $t$ has a link to an article $a$, all tweets that are retweeting $t$ considered linked to $a$.
+The same counts for tweets that are in responds to $t$, they will also be linked to $n$.
+\item \textbf{Content-based strategy}
+	\subitem \textbf{Bag of words}, in this method a tweet is represented as a vector of word frequencies.
+For a news article we can do the same thing.
+To link an article to a tweet we need to calculate the similarity between the tweet and the article and pick the one with the highest similarity.
+The similarity is calculated by the $TF \times IDF$ (Term Frequency times Inverse Document Frequency): the number of times a word from the tweet occurs in a news article, multiplied by the logarithm of the total number of articles over the number of articles the word occurs in.
+	\subitem \textbf{Hashtag-based} is based upon the same concept as the Bag of words method.
+The difference here is that we do not consider the words in the article but we are only interested in the hashtags in the tweet for our representation of the tweet.
+	\subitem \textbf{Entity-based} is also based upon the Bag of words method.
+The entity-based method does not consider words in an article.
+It relies on the entities that are mentioned in the article to make a vector to represent the article.
+\end{enumerate}
+Using these method a broader context can be created.
+This still is not much more useful than the tweet on its own.
+For the article to be actually useful the topics of the articles have to be extracted.
+To do this Natural Language Processing and machine learning can be used to extract the entities from the article.
+OpenCalais\footnote{www.opencalais.com} is a web service that does just that.
+It returns not only the entities, it will also return facts and events hidden in the text, which will make the result much more useful.
 \subsection{Sentiment analysis}

### 2014-03-03 authorinstr_2.tex
Start User classification

@@
 \subsection{User Classification}
+User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
+In this chapter we will discuss some issues concerning User Classification and some use-cases.
 
+\subsubsection{User Classification Issues}
+\textbf{Context}
 \subsection{Tag based analysis}
@@
 \begin{itemize}
-	%TODO Temporal en Twittercentric uitwerken.
-  \item Temporal:
+  \item Temporal: The characteristics of the volume over the time $T_e$ associated with an event. 
   \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
   \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
-  \item Twitter-centric: 
+  \item Twitter-centric: Some activities behave like an event but are Twitter-centric.(e.g. Tweets like 'Goodmorning!') These activities need to be filtered. 
 \end{itemize}
-%TODO Weka toolkit uitzoeken
+
 With this list of features two event-classifiers are trained using two different techniques.
-The first classifier is trained using the "WEKA tookit", in the second classifier the  Naive-Bayes technique is used.
+The first classifier is trained using the "WEKA tookit"\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, in the second classifier the  Naive-Bayes technique is used.
 According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.

### 2014-03-04 authorinstr_2.tex
Klein extra stuk

@@
 \subsubsection{User Classification Issues}
-\textbf{Context}
+\textbf{Context}\\
+To classify users on their tweets is it useful to extract the context of the content of a tweet.
+Some hashtag $x$ could have a different context in two tweets.
+So extra information about the content of a tweet is needed.
+For instance \cite{userclasst} uses mentions of (members of) political parties to deduce if a certain hashtag is used in a political context.
+\\\\
+\textbf{Profile}\\
+Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
+According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio.
+Furthermore etnicity and gender are far more difficult to extract.
 \subsection{Tag based analysis}

### 2014-03-04 authorinstr_2.tex
sentiment part1

--- 2014-03-03 authorinstr_2.tex
@@
 They linked tweets to mainstream news networks like CNN, BBC and New York Times.
-\\
+
 Linking to just news articles narrows the problem significantly, however, actually linking the tweets and the new articles still is an issue.
@@
 It returns not only the entities, it will also return facts and events hidden in the text, which will make the result much more useful.
+\newpage
 \subsection{Sentiment analysis}
+Sentiment analysis or opinion mining is "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
+This body of text can very well be a tweet, and that combined with the popularity of microblogging amongst internet users, gives a very interesting body of knowledge.
+But in order to get to that knowledge the data has to be analyzed fist.
+The most important and most obvious issue is how to extract an opinion from a tweet. In the next part we will discuss a few ways to extract an opinion from a tweet.
+\subsubsection{Semantics }
+The most important way to extract a sentiment from a tweet is by analyzing the semantics.
+After all, tweets are written text.
+The tweets can be labeled using machine learning algorithms.
+Pang et al.
+\cite{machineLearning} have done a comparative study of three standard machine learning algorithms:
+\begin{enumerate}
+\item \textbf{Naive Bayes} is a fair simple classifier that operates under the assumption that the presents or absence of features does not relate to the presents of other features.
+If we apply that on Twitter we would get $c = \arg\max_{c\in C} P(c|w)$ where $c$ is a sentiment class, $C$ the collection of sentiment classes and $w$ is a tweet.
+\cite{sentAnalysis}
+\item \textbf{Maximum Entropy} is a model that, unlike Bayes, does not make an independence assumption.
+It operates under the philosophy that "we should choose the model making the fewest assumptions about the data while still remaining consistent with it".\cite{machineLearning} \\
+The formula is of the form $P(c|d) = \frac{1}{Z(d)}\exp(\Sigma_i \lambda_{i,c}F_{i,c}(d,c))$, where $Z(d)$ is a normalization function, $\lambda_{i,c}$ a weighted vector determining the significance of the feature and $F_{i,c}$ is a class/feature function.
+\item \textbf{Support Vector Machine} is fundamentally different from Naive Bayes and Max Entropy because it is not a probabilistic model.
+The basic idea behind a support vector machine is that a vector is trained to separate the sentiments.
+Not only will it separate the training data, it will do so at the largest possible margin.
+%TODO write more shit
+\end{enumerate}
+
+\newpage
 \subsection{Concept extraction}

### 2014-03-04 authorinstr_2.tex

@@
 \subsection{User Classification}
+User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
+In this chapter we will discuss some issues concerning User Classification and some use-cases.
 
+\subsubsection{User Classification Issues}
+\textbf{Context}\\
+To classify users on their tweets is it useful to extract the context of the content of a tweet.
+Some hashtag $x$ could have a different context in two tweets.
+So extra information about the content of a tweet is needed.
+For instance \cite{userclasst} uses mentions of (members of) political parties to deduce if a certain hashtag is used in a political context.
+\\\\
+\textbf{Profile}\\
+Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
+According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio.
+Furthermore etnicity and gender are far more difficult to extract.
 \subsection{Tag based analysis}

### 2014-03-04 authorinstr_2.tex
claiming tag based
sentiment

@@
 It returns not only the entities, it will also return facts and events hidden in the text, which will make the result much more useful.
-\newpage
+
 \subsection{Sentiment analysis}
@@
 Not only will it separate the training data, it will do so at the largest possible margin.
-%TODO write more shit
+\end{enumerate}
+It turns out that over the whole the Support Vector Machine performs the best in the sentiment analysis\cite{machineLearning}. The differences, however, are not substantially large.
+
+\subsubsection{Emoticons}
+Other than semantical analysis we can also use other data from tweets.
+A good sentiment indicator are emoticons.
+Twitter users use emoticons (e.g.
+":-)", ":(" or "=(") to indicate their mood.\cite{twitterSentiment} Since the number of emoticons is limited and therefor a sentiment can be assigned easily, the information from the emoticons can be leveraged in two ways
+\begin{enumerate}
+\item \textbf{Labeling:} The emoticons can be used to assign a sentiment to a tweet.
+This can be a very useful asset to take into account when assigning sentiments.
+The emoticons can be considered unigrams for some other classifier.
+There they will be strong evidence for a certain sentiment.
+\item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus.
+Twitter can be queried for "positive" emoticons and "negative" emoticons and by assuming the emoticon reflects the sentiment of the tweet, it can be labeled accordingly.\cite{moodLens}
 \end{enumerate}
 
-\newpage
 \subsection{Concept extraction}

### 2014-03-04 authorinstr_2.tex
commit to pull
API added

@@
 
+\newpage
+
 \section{Data}
@@
 \subsection{Twitter API}
+
+When Twitter was conceived, the developers decided that to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
+beneficial to both Twitter's popularity and alot of its users, including researchers.
+
+An overview of the API structure and some useful fields:
+\begin{enumerate}
+\item \textbf{Tweets} The short messages sent by users
+	\subitem \textbf{Coordinates} Retrieves the longitude and latitude position from where a specified tweet has been sent
+	\subitem \textbf{Entities} Retrieves the entities (url, hashtag, etc.) that are embedded into the tweet
+	\subitem \textbf{Lang} Retrieves the language in which a tweet has been sent
+	\subitem \textbf{User} Retrieves the user that sent a tweet
+\item \textbf{Users} The accounts that send tweets
+	\subitem \textbf{Description} Retrieves the description that the user defined for his account
+	\subitem \textbf{Location} Retrieves the location that the user defined for his account
+	\subitem \textbf{Status} Retrieves, if possible, the user's latest tweet
+\item \textbf{Entities} Images, hashtags and other entities that tweets can hold
+	\subitem \textbf{Hashtags} Retrieves the hashtags that have been parset out of a tweet
+	\subitem \textbf{Media} Retrieves the media that is associated with a tweet
+	\subitem \textbf{urls} Retrieves the urls embedded in a tweet
+	\subitem \textbf{user\_mentions} Retrieves the users that have been mentioned in a tweet
+\item \textbf{Places} Predefined places on Twitter that users can associate with
+	\subitem \textbf{Country} Retrieves the country associated with a place
+	\subitem \textbf{Full\_name} Retrieves the full name of a place, for example Kanses ``City, Kansas''
+	\subitem \textbf{Place\_type} Retrieves the type of a place, for example ``city''
+\end{enumerate}
+
+When the above fields are combined, it is possible to create sets of Tweets that fulfill a certain specification. These sets can be used to extract information.
+No matter how specific you can define your search, sometimes you need a random sample of tweets to analyse. For this purpose, Twitter has a stream that
+third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.
+
+The following of this article describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information
+can be applied to.
+
+\newpage
+
 \section{Single tweet analysis}
@@
 Furthermore etnicity and gender are far more difficult to extract.
+
 \subsection{Tag based analysis}
+
+Twitter allows their users to contribute their own social annotations to their tweets in the form of tags. These tags can be arbitrarily generated by users 
+which make them hold interesting information about both the tweet and the user that posted it.
+
+\begin{enumerate}
+\item \textbf{Linear-Weighted Hybrid}\\
+
+%TODO: Technische stuff begrijpen zodat ik die hier neer kan zetten + bibliography laten doorverwijzen
+
+\item \textbf{Pair-Wise Interaction Tensor Factorization} The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
+been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter.
+
+\end{enumerate}
+
 \subsection{Event identification}
@@
 Furthermore \cite{earthq}'s system detects an earthquake 10 minutes after happening and sends a message within a minute after detection.
+
+\newpage
+
 \section{Conclusion}
+
+\newpage
 

### 2014-03-05 authorinstr_2.tex
last changes

--- 2014-03-04 authorinstr_2.tex
@@
 \subsection{Data enrichment}
-At the very basis of a tweet is data enrichment.
+At the very basis of the analysis of a tweet is data enrichment.
 Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about.
@@
 For humans this is done by linking the information from the tweet to earlier acquired knowledge.
-\subsubsection{Data enrichment issues}
+The same thing can be done by computers.
+\subsubsection{Context creation}
 The problem of linking tweets to another source of information poses the biggest issue in data enrichment.
@@
 Fortunately, Kwak et al.
-have shown that the topic of over 85\% of the of the tweet is related to news \cite{newsmedia}.
+have shown that the topic of over 85\% of the of the tweets is related to news \cite{newsmedia}.
 This knowledge can be leveraged to create a context for most of the tweets.
-This is what what Abel et al.
+This is what Abel et al.
 proposed to do\cite{enrichmentForProfiling}.
@@
 \item \textbf{URL-based strategy}\\
-This strategy is based upon the observation that many tweets contains URLs. Usually these URLs refer to news articles the tweets are closely related to.
-	\subitem \textbf{Strict URL-based} defines an article and a tweet as related when the tweet contains an URL to that news article.
+This strategy is based upon the observation that many tweets contains URLs. Usually these URLs refer to news articles the tweets are closely related to. Two URL-based strategies are proposed
+	\subitem \textbf{Strict URL-based} defines an article $a$ and a tweet $t$ to be related when $t$ contains an URL to $a$.
 	\subitem \textbf{Lenient URL-based}, this method is an extension of the strict URL-based method.
-This extension entails that if a tweet $t$ has a link to an article $a$, all tweets that are retweeting $t$ considered linked to $a$.
-The same counts for tweets that are in responds to $t$, they will also be linked to $n$.
-\item \textbf{Content-based strategy}
+This extension entails that if a tweet $t$ has a link to an article $a$, all tweets that are retweeting $t$ are considered linked to $a$.
+The same counts for tweets that are in responds to $t$, these tweets will also be considered linked to $a$.
+\item \textbf{Content-based strategy}\\
+Content-based strategies rely on the idea of finding as much similarity as possible between the content of a tweet and the content of a news article.
+The most similar tweet-article pair is considered to be related and therefor they are linked.
 	\subitem \textbf{Bag of words}, in this method a tweet is represented as a vector of word frequencies.
-For a news article we can do the same thing.
+For a news article we can also create a vector the represent it.
 To link an article to a tweet we need to calculate the similarity between the tweet and the article and pick the one with the highest similarity.
 The similarity is calculated by the $TF \times IDF$ (Term Frequency times Inverse Document Frequency): the number of times a word from the tweet occurs in a news article, multiplied by the logarithm of the total number of articles over the number of articles the word occurs in.
+\cite{tfidf}
 	\subitem \textbf{Hashtag-based} is based upon the same concept as the Bag of words method.
-The difference here is that we do not consider the words in the article but we are only interested in the hashtags in the tweet for our representation of the tweet.
+The difference is that we do not consider the words in the article, instead we only use the hashtags in the representation of a tweet to calculate the $TF \times IDF$ with.
 	\subitem \textbf{Entity-based} is also based upon the Bag of words method.
@@
 Sentiment analysis or opinion mining is "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
-This body of text can very well be a tweet, and that combined with the popularity of microblogging amongst internet users, gives a very interesting body of knowledge.
+This body of text can very well be a tweet, and that combined with the popularity of microblogging amongst internet users, makes Twitter a very interesting body of knowledge about the opinion of a large group of people.
 But in order to get to that knowledge the data has to be analyzed fist.
@@
 \subsubsection{Semantics }
-The most important way to extract a sentiment from a tweet is by analyzing the semantics.
+The most important way to extract a sentiment from a tweet is by analyzing its semantics.
 After all, tweets are written text.
-The tweets can be labeled using machine learning algorithms.
+A sentiment can be assigned to a tweet using machine learning algorithms.
 Pang et al.
-\cite{machineLearning} have done a comparative study of three standard machine learning algorithms:
+\cite{machineLearning} have done a comparative study of three standard machine learning algorithms for sentiment analysis:
 \begin{enumerate}
@@
 \end{enumerate}
-It turns out that over the whole the Support Vector Machine performs the best in the sentiment analysis\cite{machineLearning}. The differences, however, are not substantially large.
+It turns out that over the whole the Support Vector Machine performs the best on the sentiment analysis\cite{machineLearning}. The differences, however, are not substantially large.
 
@@
 Twitter users use emoticons (e.g.
-":-)", ":(" or "=(") to indicate their mood.\cite{twitterSentiment} Since the number of emoticons is limited and therefor a sentiment can be assigned easily, the information from the emoticons can be leveraged in two ways
+":-)", ":(" or "=(") to indicate their mood.\cite{twitterSentiment} Since the number of emoticons is limited a sentiment can easily be assigned manually.
+The information from the emoticons can be leveraged in two ways
 \begin{enumerate}
 \item \textbf{Labeling:} The emoticons can be used to assign a sentiment to a tweet.
-This can be a very useful asset to take into account when assigning sentiments.
-The emoticons can be considered unigrams for some other classifier.
+This can be a very useful asset to take into account when assigning a sentiment to a tweet.
+The emoticons can be considered unigrams feature for some classifier.
 There they will be strong evidence for a certain sentiment.
-\item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus.
-Twitter can be queried for "positive" emoticons and "negative" emoticons and by assuming the emoticon reflects the sentiment of the tweet, it can be labeled accordingly.\cite{moodLens}
+\item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus for a supervised learning algorithm.
+Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labeled accordingly.\cite{moodLens}
 \end{enumerate}
-
+We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
+\subsubsection{Usage}
+The possibilities of sentiment analysis are not too hard to imagine.
+Every company wants to know how their newly launched product is doing, film makes want to know what people think about their new movie and politicians want to know how they are doing for the next elections.
+Using sentiment analysis all this information will become available\cite{machineLearning}.
 \subsection{Concept extraction}
@@
 Furthermore etnicity and gender are far more difficult to extract.
+
 \subsection{Tag based analysis}
+
+Twitter allows their users to contribute their own social annotations to their tweets in the form of tags. These tags can be arbitrarily generated by users 
+which make them hold interesting information about both the tweet and the user that posted it.
+
 \subsection{Event identification}

### 2014-03-05 authorinstr_2.tex

@@
 
+\begin{enumerate}
+\item \textbf{Linear-Weighted Hybrid}\\
+
+%TODO: Technische stuff begrijpen zodat ik die hier neer kan zetten + bibliography laten doorverwijzen
+
+\item \textbf{Pair-Wise Interaction Tensor Factorization} The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
+been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter.
+
+\end{enumerate}
+
 \subsection{Event identification}

### 2014-03-05 authorinstr_2.tex
User Classification andere aanpak

--- 2014-03-04 authorinstr_2.tex
@@
 User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
-In this chapter we will discuss some issues concerning User Classification and some use-cases.
+In this chapter we will discuss some features used to classify users and some use-cases.
 
-\subsubsection{User Classification Issues}
-\textbf{Context}\\
-To classify users on their tweets is it useful to extract the context of the content of a tweet.
-Some hashtag $x$ could have a different context in two tweets.
-So extra information about the content of a tweet is needed.
-For instance \cite{userclasst} uses mentions of (members of) political parties to deduce if a certain hashtag is used in a political context.
+\subsubsection{Classification Features}
+To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
+\\\\
+\textbf{Linguistics}\\
+TODO
+\\\\
+\textbf{Interaction Profiles}\\
+Users interaction profiles is a profile created by \cite{pol} to capture interactions between users and other accounts.
+An interaction is a retweet or a reply.
+\cite{usermachine} also uses friend accounts as a measurement in interaction between users.
+A friend account of user $x$ is an account that is followed by user $x$.
+\\\\
+\textbf{Tweeting Behavior}\\
+Tweeting behavior is a set of characteristics which shows us the way a users interacts with twitter.
+Things like the average number of messages, number of replies \& number of friends seems a good quantifier for classification.
+According to \cite{usermachine} these features are useful but not really discriminative.
 \\\\
@@
 According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio.
-Furthermore etnicity and gender are far more difficult to extract.
+Furthermore \cite{usermachine} was able to extract a gender for 80\% of the users, but with a very low accuracy.
+\cite{usermachine} also researched the profile picture/avatar of twitter users.
+They found out that these pictures can often be misleading as 20\% of the found profile pictures was not the owner but another person such as a celebrity.
+
+\subsubsection{Usecase: Predicting Political Preferences}
 

### 2014-03-06 authorinstr_2.tex
Klein stukje

@@
 \textbf{Linguistics}\\
-TODO
+Linguistics can say a lot about the interests of a user.
+To classify a user Prototipical Words(PW's) can be used.
+\cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$.
+In a twitter-context also Prototipical Hashtags can be used.
 \\\\
@@
 \subsubsection{Usecase: Predicting Political Preferences}
-
+During election time 
 \subsection{Tag based analysis}

### 2014-03-08 authorinstr_2.tex
weinig meer

--- 2014-03-05 authorinstr_2.tex
@@
 
-\newpage
-
 \section{Single tweet analysis}
@@
 
+\subsubsection{Hidden topic discovery}
+Another way to deal with the sparseness of the data in a tweet is hidden topic discovery.
+
 \subsection{Sentiment analysis}
@@
 \subsection{Concept extraction}
+Concept extraction is not a completely new concept. We already mentioned it in the previous sections. Concept extraction a very general way to give more meaning to a corpus of text. 
 \subsection{Metadata analysis (opt)}
@@
 User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
-In this chapter we will discuss some features used to classify users and some use-cases.
+In this chapter we will discuss some issues concerning User Classification and some use-cases.
 
-\subsubsection{Classification Features}
-To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
-\\\\
-\textbf{Linguistics}\\
-TODO
-\\\\
-\textbf{Interaction Profiles}\\
-Users interaction profiles is a profile created by \cite{pol} to capture interactions between users and other accounts.
-An interaction is a retweet or a reply.
-\cite{usermachine} also uses friend accounts as a measurement in interaction between users.
-A friend account of user $x$ is an account that is followed by user $x$.
-\\\\
-\textbf{Tweeting Behavior}\\
-Tweeting behavior is a set of characteristics which shows us the way a users interacts with twitter.
-Things like the average number of messages, number of replies \& number of friends seems a good quantifier for classification.
-According to \cite{usermachine} these features are useful but not really discriminative.
+\subsubsection{User Classification Issues}
+\textbf{Context}\\
+To classify users on their tweets is it useful to extract the context of the content of a tweet.
+Some hashtag $x$ could have a different context in two tweets.
+So extra information about the content of a tweet is needed.
+For instance \cite{userclasst} uses mentions of (members of) political parties to deduce if a certain hashtag is used in a political context.
 \\\\
@@
 According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio.
-Furthermore \cite{usermachine} was able to extract a gender for 80\% of the users, but with a very low accuracy.
-\cite{usermachine} also researched the profile picture/avatar of twitter users.
-They found out that these pictures can often be misleading as 20\% of the found profile pictures was not the owner but another person such as a celebrity.
-
-\subsubsection{Usecase: Predicting Political Preferences}
+Furthermore etnicity and gender are far more difficult to extract.
 

### 2014-03-09 authorinstr_2.tex
Wat userclassification toegevoegd.

--- 2014-03-06 authorinstr_2.tex
@@
 \subsubsection{Usecase: Predicting Political Preferences}
-During election time 
+During election time it can be useful to predict the political preferences of a user.
+In \cite{pol} a solution to this problem is presented.
+As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
+
+To achieve this a combination of (political) hashtags in combination with twitter activities is used.
+To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts.
+Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.
 \subsection{Tag based analysis}

### 2014-03-09 authorinstr_2.tex
niet veel

@@
 Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.
+
+To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties. 
 \subsection{Tag based analysis}
@@
 %TODO uitwerken
-  \item Immediate Resource Leaves: TODO
-  \item 1-Step Resource Leaves 
-  \item DBPedia Concepts 
+  \item Immediate Resource Leaves: Use only the URI which are most indicative of an event. This feature only uses literals and resources within the URI of an event. 
+  \item 1-Step Resource Leaves: Use all literals and resources within 1 step from the URI of an event. 
+  \item DBPedia Concepts: Also uses all the concepts from DBPedia 
 \end{itemize}

### 2014-03-10 authorinstr_2.tex
test

--- 2014-03-08 authorinstr_2.tex
@@
 At the very basis of the analysis of a tweet is data enrichment.
-Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about.
+Because the length of a tweet is restricted to 140 characters, the users of Twitter use language in creative ways.
+This way of communicating makes it sometimes, even for humans, hard to understand what a tweet is about.
 To get a better understanding of the meaning of a tweet, a context is needed.
-For humans this is done by linking the information from the tweet to earlier acquired knowledge.
+For humans this is done by linking the concepts from the tweet to earlier acquired knowledge.
 The same thing can be done by computers.
+Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
+\subsubsection{Concept extraction}
+In this case by concepts we mean named entities such as names of locations, people and organizations.
+To recognize these entities multiple learning algorithms or even combinations of learning algorithms have been proposed.
+The most common is statistical learning.
+Think of algorithms like Maximum Entropy Models, Hidden Markov Models or neural networks.
+Other proposed algorithms are AdaBoost.MH, employed memory-based learning, transformation-based learning, support vector machines and conditional random fields.
+All of them in decreasing frequency of use.\cite{EntityRecognition} Florian et al.
+have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or location.
+Then Abel et al.
+propose to use the RDF.\cite{AdaptiveSearch} In that case sources from the Semantic Web (e.g.
+DBpedia \footnote{"http://dbpedia.org"}) can now be leveraged to enrich the data.
+These sources already contain a lot of information about the connections between concepts.
 \subsubsection{Context creation}
@@
 It returns not only the entities, it will also return facts and events hidden in the text, which will make the result much more useful.
-
-\subsubsection{Hidden topic discovery}
-Another way to deal with the sparseness of the data in a tweet is hidden topic discovery.
 

### 2014-03-10 authorinstr_2.tex

@@
 \subsubsection{Usecase: Predicting Political Preferences}
-During election time 
+During election time it can be useful to predict the political preferences of a user.
+In \cite{pol} a solution to this problem is presented.
+As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
+
+To achieve this a combination of (political) hashtags in combination with twitter activities is used.
+To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts.
+Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.
+
+To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties. 
 \subsection{Tag based analysis}

### 2014-03-10 authorinstr_2.tex
concept extraction

@@
 Then Abel et al.
-propose to use the RDF.\cite{AdaptiveSearch} In that case sources from the Semantic Web (e.g.
-DBpedia \footnote{"http://dbpedia.org"}) can now be leveraged to enrich the data.
-These sources already contain a lot of information about the connections between concepts.
+propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g.
+DBpedia \footnote{http://dbpedia.org/}) can now be leveraged to enrich the data.
+Another advantage of using RDF is that RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}.
+Because W3C recommends to use this model, most likely a lot of other sources also use this model.
+This will give a much bigger knowledge base to enrich the data from.
 \subsubsection{Context creation}
@@
 Using sentiment analysis all this information will become available\cite{machineLearning}.
-\subsection{Concept extraction}
-Concept extraction is not a completely new concept. We already mentioned it in the previous sections. Concept extraction a very general way to give more meaning to a corpus of text. 
 \subsection{Metadata analysis (opt)}

### 2014-03-10 authorinstr_2.tex
User modelling + wat andere dingen.

@@
 
+\newpage
+
 \section{Single tweet analysis}
@@
 At the very basis of the analysis of a tweet is data enrichment.
-Because the length of a tweet is restricted to 140 characters, the users of Twitter use language in creative ways.
-This way of communicating makes it sometimes, even for humans, hard to understand what a tweet is about.
+Because the length of a tweet is restricted to 140 characters the users of Twitter use language in creative ways that sometimes make it, even for humans, hard to understand what a tweet is about.
 To get a better understanding of the meaning of a tweet, a context is needed.
-For humans this is done by linking the concepts from the tweet to earlier acquired knowledge.
+For humans this is done by linking the information from the tweet to earlier acquired knowledge.
 The same thing can be done by computers.
-Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
-\subsubsection{Concept extraction}
-In this case by concepts we mean named entities such as names of locations, people and organizations.
-To recognize these entities multiple learning algorithms or even combinations of learning algorithms have been proposed.
-The most common is statistical learning.
-Think of algorithms like Maximum Entropy Models, Hidden Markov Models or neural networks.
-Other proposed algorithms are AdaBoost.MH, employed memory-based learning, transformation-based learning, support vector machines and conditional random fields.
-All of them in decreasing frequency of use.\cite{EntityRecognition} Florian et al.
-have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or location.
-Then Abel et al.
-propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g.
-DBpedia \footnote{http://dbpedia.org/}) can now be leveraged to enrich the data.
-Another advantage of using RDF is that RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}.
-Because W3C recommends to use this model, most likely a lot of other sources also use this model.
-This will give a much bigger knowledge base to enrich the data from.
 \subsubsection{Context creation}
@@
 Using sentiment analysis all this information will become available\cite{machineLearning}.
+\subsection{Concept extraction}
 \subsection{Metadata analysis (opt)}
@@
 \subsection{Statistics}
-\subsection{User Modelling}
+
 \subsection{User Classification}
 User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
-In this chapter we will discuss some features used to classify users and some use-cases.
+In this chapter we will discuss User Models, some features used to classify users and some use-cases.
+\subsubsection{User Models}
+Before it is possible to classify a user, it is useful to create a model of a user. In their paper Fabel et al compare the following three ways to model a user. \cite{usermodel}
+\begin{itemize}
+\item Hashtag-based
+\item Entity-based
+\item Topic-based
+
+\end{itemize}
+After all these approaches are used on the same dataset it appears that the variety of entity-based profiles was much higher than the hashtag based approach.
+\cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.
 
@@
 
-To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties. 
+To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties.) After this all information is combined to predict a political party for each user. 
 \subsection{Tag based analysis}

### 2014-03-10 authorinstr_2.tex
Kleine toevoegingen
API revised

@@
 
-When Twitter was conceived, the developers decided that to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
+When Twitter was conceived, the creators chose to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
 beneficial to both Twitter's popularity and alot of its users, including researchers.
@@
 \begin{enumerate}
-\item \textbf{Tweets} The short messages sent by users
-	\subitem \textbf{Coordinates} Retrieves the longitude and latitude position from where a specified tweet has been sent
-	\subitem \textbf{Entities} Retrieves the entities (url, hashtag, etc.) that are embedded into the tweet
-	\subitem \textbf{Lang} Retrieves the language in which a tweet has been sent
-	\subitem \textbf{User} Retrieves the user that sent a tweet
-\item \textbf{Users} The accounts that send tweets
-	\subitem \textbf{Description} Retrieves the description that the user defined for his account
-	\subitem \textbf{Location} Retrieves the location that the user defined for his account
-	\subitem \textbf{Status} Retrieves, if possible, the user's latest tweet
+\item \textbf{Tweets} The short messages consisting of 140 characters sent by users
+	\subitem \textbf{Coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
+	\subitem \textbf{Entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
+	\subitem \textbf{Lang} Returns the language in which a tweet has been sent
+	\subitem \textbf{User} Returns the user that sent a tweet
+\item \textbf{Users} The users that send the tweets
+	\subitem \textbf{Description} Returns the description that the user defined for his account
+	\subitem \textbf{Location} Returns the location that the user defined for his account
+	\subitem \textbf{Status} Returns, if possible, the user's latest tweet
 \item \textbf{Entities} Images, hashtags and other entities that tweets can hold
-	\subitem \textbf{Hashtags} Retrieves the hashtags that have been parset out of a tweet
-	\subitem \textbf{Media} Retrieves the media that is associated with a tweet
-	\subitem \textbf{urls} Retrieves the urls embedded in a tweet
-	\subitem \textbf{user\_mentions} Retrieves the users that have been mentioned in a tweet
+	\subitem \textbf{Hashtags} Returns the hashtags that have been parset out of a tweet
+	\subitem \textbf{Media} Returns the media that is associated with a tweet
+	\subitem \textbf{urls} Returns the urls embedded in a tweet
+	\subitem \textbf{user\_mentions} Returns the users that have been mentioned in a tweet
 \item \textbf{Places} Predefined places on Twitter that users can associate with
-	\subitem \textbf{Country} Retrieves the country associated with a place
-	\subitem \textbf{Full\_name} Retrieves the full name of a place, for example Kanses ``City, Kansas''
-	\subitem \textbf{Place\_type} Retrieves the type of a place, for example ``city''
+	\subitem \textbf{Country} Returns the country associated with a place
+	\subitem \textbf{Full\_name} Returns the full name of a place, for example Kanses ``City, Kansas''
+	\subitem \textbf{Place\_type} Returns the type of a place, for example ``city''
 \end{enumerate}
 
-When the above fields are combined, it is possible to create sets of Tweets that fulfill a certain specification. These sets can be used to extract information.
-No matter how specific you can define your search, sometimes you need a random sample of tweets to analyse. For this purpose, Twitter has a stream that
+When the above fields are combined, it is possible to create datasets of Tweets that fulfill a certain specification. 
+These sets can then be used to extract specific information. However, defining your own dataset may introduce a certain bias, 
+and sometimes you need a random sample of tweets to analyse. For this purpose, Twitter has a streaming function that
 third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.
@@
 propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g.
-DBpedia \footnote{http://dbpedia.org/}) can now be leveraged to enrich the data.
+DBpedia \footnote{http://dbpedia.
+org/}) can now be leveraged to enrich the data.
 Another advantage of using RDF is that RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}.
@@
 \end{itemize}
-%TODO afmaken
-
+After this a Feature Vector is composed, for tweets all stop words are removed from the bag of words a tweet is represented as.
+Furthermore all stopwords are removed and everything is normalized to lowercase.
+\cite{eventalign} Then a labeling function is used to label the event.
 \subsubsection{Usecase: Earthquake Detection}

### 2014-03-10 authorinstr_2.tex
Tag Based Update 1

@@
 \item \textbf{Tweets} The short messages consisting of 140 characters sent by users
-	\subitem \textbf{Coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
-	\subitem \textbf{Entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
-	\subitem \textbf{Lang} Returns the language in which a tweet has been sent
-	\subitem \textbf{User} Returns the user that sent a tweet
+	\subitem \textbf{coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
+	\subitem \textbf{entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
+	\subitem \textbf{lang} Returns the language in which a tweet has been sent
+	\subitem \textbf{user} Returns the user that sent a tweet
 \item \textbf{Users} The users that send the tweets
-	\subitem \textbf{Description} Returns the description that the user defined for his account
-	\subitem \textbf{Location} Returns the location that the user defined for his account
-	\subitem \textbf{Status} Returns, if possible, the user's latest tweet
+	\subitem \textbf{description} Returns the description that the user defined for his account
+	\subitem \textbf{location} Returns the location that the user defined for his account
+	\subitem \textbf{status} Returns, if possible, the user's latest tweet
 \item \textbf{Entities} Images, hashtags and other entities that tweets can hold
-	\subitem \textbf{Hashtags} Returns the hashtags that have been parset out of a tweet
-	\subitem \textbf{Media} Returns the media that is associated with a tweet
+	\subitem \textbf{hashtags} Returns the hashtags that have been parset out of a tweet
+	\subitem \textbf{media} Returns the media that is associated with a tweet
 	\subitem \textbf{urls} Returns the urls embedded in a tweet
@@
 \item \textbf{Places} Predefined places on Twitter that users can associate with
-	\subitem \textbf{Country} Returns the country associated with a place
-	\subitem \textbf{Full\_name} Returns the full name of a place, for example Kanses ``City, Kansas''
-	\subitem \textbf{Place\_type} Returns the type of a place, for example ``city''
+	\subitem \textbf{country} Returns the country associated with a place
+	\subitem \textbf{full\_name} Returns the full name of a place, for example Kanses ``City, Kansas''
+	\subitem \textbf{place\_type} Returns the type of a place, for example ``city''
 \end{enumerate}
@@
 Twitter allows their users to contribute their own social annotations to their tweets in the form of tags. These tags can be arbitrarily generated by users 
-which make them hold interesting information about both the tweet and the user that posted it.
+which make them hold interesting information about both the tweet and the user that posted it. There are two dominant techniques that are currently being
+used by researchers to model the information of tagged based analysis, The Linear-Weighted Hybrid Model, and the Pair-wise Interaction Tensor Factorisation Model.
 
@@
 
-%TODO: Technische stuff begrijpen zodat ik die hier neer kan zetten + bibliography laten doorverwijzen
+The Linear-Weighted Hybrid model uses the tags as recommendation components whose output is a weighted sum of components $\kappa_1$ through $\kappa_k$. 
+Each component $\kappa_i$ has its own value between 0 and 1 computed by the function $\phi_i (u,q,r)$, and a corresponding weight $\alpha_i$, also between
+0 and 1. The sum of all weights $\alpha_i$ has to be 1.
+
+Therefore, the hybrid model is defined as the function $\varphi (u, q, r) = \sum\limits_{i = 1}^k \alpha_i \phi_i (u,q,r)$
+
+All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique. A subset is used as a holdout set, and a vector
+gets created with random weights that sum to 1. The recommender then modifies the vector over the holdout set to train the algorithm until it reaches
+a stable point. The algorithm then restarts to avoid local minima.
 

### 2014-03-11 authorinstr_2.tex
Intro

@@
 \section{Introduction}
+
+Microblogging has grown out to be one of the most interesting forms of social media. One of its most popular implementations has to be Twitter, where
+users can share short messages, called Tweets, with every other user. The limitation in characters forces users to 
+compress all their information into a small message, making them extra interesting to analyse. These Tweets often contain information broadcasted by the user in
+the form of opinions, emotions, interests, etc. One of the biggest challenges is finding a way to extract the intended information from these Tweets. Once
+the information is extracted however, the possible applications are endless. This paper is dedicated to combining succesful techniques and useful applications
+of these social web data analytics. In the following section, Twitters API gets introduced which will show that the platform already offers great tools
+and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, two entire sections will be dedicated to all sorts
+of techniques that are being used to extract this information. One section will focus on single tweets, and the following on sets of multiple Tweets. Both
+of these sections will involve several usecases for certain techniques.
+
+%TODO: Add what the conclusion will say
 
@@
 
-\item \textbf{Pair-Wise Interaction Tensor Factorization} The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
+\item \textbf{Pair-Wise Interaction Tensor Factorization}
+
+The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
 been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter. 
+The adaptation involves changing the roles of resources and tags with respect to each other.
+
+Our adaptation of the model to resource
+recommendation simply exchanges the roles of resources and tags with respect to each
+other. This model-based approach generates a set of factor matrices which resembles
+a special case of the Tucker decomposition of a tensor. The tensor itself is not directly
+induced by the data, but rather reflects a ranking over the resources for each user-tag
+pair. Thus, it is important to note that this model is applicable only to the special case of
+tag-based resource recommendation, and not for resource recommendation tasks with
+other requirements.
+The model is built by considering observations in the data of the form (u, r+ , r− , t),
+where (u, r+ , t) is a triple which is found in the data (a positive example of resource
+selection) and (u, r− , t) is a triple not found in the data (a negative example of re-
+source selection). An iterative gradient-descent algorithm is employed to optimize a116
+J. Gemmell et al.
+ranking function that prefers positive examples in the data over negative ones. Each of
+four related matrices is updated until convergence is found. The matrices represent the
+U
+T
+factor-reduced components of the specialized tensor factorization M = Uk Rk
++Tk Rk
+,
+U
+where Uk is the user factor matrix, Tk is the tag factor matrix, Rk is the resource factor
+T
+matrix with respect to users and Rk
+is the resource factor matrix with respect to tags, k
+is the selected number of factors, and M is the personalized resource-ranking tensor.
+Generating a resource recommendation for a given user u and tag t is simply a
+matter of referring to the appropriate user-tag column of the ranking tensor M . The
+relevance score of a resource given a user-tag pair is calculated as: φ(u, {t}, r) =
 

### 2014-03-11 authorinstr_2.tex
Tag based update 2

@@
 
-Our adaptation of the model to resource
-recommendation simply exchanges the roles of resources and tags with respect to each
-other. This model-based approach generates a set of factor matrices which resembles
-a special case of the Tucker decomposition of a tensor. The tensor itself is not directly
-induced by the data, but rather reflects a ranking over the resources for each user-tag
-pair. Thus, it is important to note that this model is applicable only to the special case of
-tag-based resource recommendation, and not for resource recommendation tasks with
-other requirements.
-The model is built by considering observations in the data of the form (u, r+ , r− , t),
-where (u, r+ , t) is a triple which is found in the data (a positive example of resource
-selection) and (u, r− , t) is a triple not found in the data (a negative example of re-
-source selection). An iterative gradient-descent algorithm is employed to optimize a116
-J. Gemmell et al.
-ranking function that prefers positive examples in the data over negative ones. Each of
-four related matrices is updated until convergence is found. The matrices represent the
-U
-T
-factor-reduced components of the specialized tensor factorization M = Uk Rk
-+Tk Rk
-,
-U
-where Uk is the user factor matrix, Tk is the tag factor matrix, Rk is the resource factor
-T
-matrix with respect to users and Rk
-is the resource factor matrix with respect to tags, k
-is the selected number of factors, and M is the personalized resource-ranking tensor.
-Generating a resource recommendation for a given user u and tag t is simply a
-matter of referring to the appropriate user-tag column of the ranking tensor M . The
-relevance score of a resource given a user-tag pair is calculated as: φ(u, {t}, r) =
+This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor. 
+The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefor only useful in the case of tag-based resource recommendation, 
+and not for resource recommendations with other requirements.
 
+To build the model, the data has to be observed in the form $(u, r+, r-, t)$ where $(u, r+, t)$ and $(u, r-, t)$ is a triple respectively
+found and not found in the dataset. A ranking function is then used to prefer positive examples over negative ones. An iterative gradient-descent
+algorithm is used to optimize this function. All four matrices will be updated until they converge. The matrices represent the factor-reduced components
+of the specialised tensor factorization:
+
+$M = U_k R_k^U + T_k R_k^T$
+
+With 
+\begin{enumerate}
+ \item $U_k$ the user factorization
+ \item $T_k$ is the tag factor matrix
+ \item $R_k^U$ is the resource factor matrix with respect to the users
+ \item $R_k^T$ is the resource factor matrix with respect to the tags
+ \item $k$ selected number of factors
+ \item $M$ the personalized resource-ranking tensor
+\end{enumerate}
+
+The relevance score of a resource can now be calculated by:
+
+$\phi (u, \{t\}, r) = \sum_{i=1}^k U_k\{u\}\{i\}R_k^U\{r\}\{i\} + T_k\{t\}\{i\}R_k^T\{r\}\{i\}$	
 \end{enumerate}

### 2014-03-11 authorinstr_2.tex
check

@@
 
-Microblogging has grown out to be one of the most interesting forms of social media. One of its most popular implementations has to be Twitter, where
-users can share short messages, called Tweets, with every other user. The limitation in characters forces users to 
-compress all their information into a small message, making them extra interesting to analyse. These Tweets often contain information broadcasted by the user in
-the form of opinions, emotions, interests, etc. One of the biggest challenges is finding a way to extract the intended information from these Tweets. Once
-the information is extracted however, the possible applications are endless. This paper is dedicated to combining succesful techniques and useful applications
-of these social web data analytics. In the following section, Twitters API gets introduced which will show that the platform already offers great tools
-and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, two entire sections will be dedicated to all sorts
-of techniques that are being used to extract this information. One section will focus on single tweets, and the following on sets of multiple Tweets. Both
-of these sections will involve several usecases for certain techniques.
+Microblogging has grown out to be one of the most interesting forms of social media.
+One of its most popular implementations has to be Twitter, where users can share short messages, called Tweets, with any other user.
+The limitation of 140 characters per Tweet forces users to compress all their information into a small message, making them extra interesting to analyze.
+These Tweets often contain information broadcasted by the user in the form of opinions, emotions, interests, etc.
+One of the biggest challenges is finding a way to extract the intended information from these Tweets.
+Once the information is extracted however, the possible applications are endless.
+This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics.
+In the following section, Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets.
+After that, two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information.
+The first section will focus on single tweets, and the second section is focused on sets of multiple Tweets.
+Both of these sections will involve several usecases for certain techniques.
 
 %TODO: Add what the conclusion will say
-
-\newpage
 
@@
 
-When Twitter was conceived, the creators chose to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
-beneficial to both Twitter's popularity and alot of its users, including researchers.
+When Twitter was founded, the creators chose to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
+beneficial to both Twitter's popularity and a lot of its users, including researchers.
 
@@
 When the above fields are combined, it is possible to create datasets of Tweets that fulfill a certain specification.
-These sets can then be used to extract specific information. However, defining your own dataset may introduce a certain bias, 
-and sometimes you need a random sample of tweets to analyse. For this purpose, Twitter has a streaming function that
-third party developers can tap into to retrieve random tweets. Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.
+These sets can then be used to extract specific information.
+However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyze.
+For this purpose, Twitter has a streaming function that third party developers can tap into to retrieve random tweets.
+Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.
 
-The following of this article describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information
-can be applied to.
+The following of this paper describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information can be applied to.
 
@@
 To recognize these entities multiple learning algorithms or even combinations of learning algorithms have been proposed.
-The most common is statistical learning.
+The most common are the statistical learning algorithms.
 Think of algorithms like Maximum Entropy Models, Hidden Markov Models or neural networks.
@@
 All of them in decreasing frequency of use.\cite{EntityRecognition} Florian et al.
-have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or location.
-Then Abel et al.
+have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or a location.
+These labels on its own are not worth a lot.
+They can be used in an application that is build to handle these labels.
+Therefore Abel et al.
 propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g.
@@
 This will give a much bigger knowledge base to enrich the data from.
+
+The whole process of building a system to extract concept from a tweet seems to be a lot of work.
+Fortunately there are services like OpenCalais\footnote{www.opencalais.com}.
+OpenCalais is a web service that can extract concepts.
+Not only does it return the entities, it will also return facts and events hidden in the text, which will make the result even more useful.
 \subsubsection{Context creation}
-The problem of linking tweets to another source of information poses the biggest issue in data enrichment.
+The problem of linking tweets to another source of information poses one the biggest issue in data enrichment.
 The tweets themselves do not provide much information.
@@
 This extension entails that if a tweet $t$ has a link to an article $a$, all tweets that are retweeting $t$ are considered linked to $a$.
-The same counts for tweets that are in responds to $t$, these tweets will also be considered linked to $a$.
+The same counts for tweets that are in responds to $t$.
+These tweets will also be considered linked to $a$.
 \item \textbf{Content-based strategy}\\
@@
 To do this Natural Language Processing and machine learning can be used to extract the entities from the article.
-OpenCalais\footnote{www.opencalais.com} is a web service that does just that.
-It returns not only the entities, it will also return facts and events hidden in the text, which will make the result much more useful.
 
 \subsection{Sentiment analysis}
-Sentiment analysis or opinion mining is "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
+Sentiment analysis or opinion mining is, as the Financial Times defines it, "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
 This body of text can very well be a tweet, and that combined with the popularity of microblogging amongst internet users, makes Twitter a very interesting body of knowledge about the opinion of a large group of people.
@@
 Pang et al.
-\cite{machineLearning} have done a comparative study of three standard machine learning algorithms for sentiment analysis:
+\cite{machineLearning} have done a study on three standard machine learning algorithms for sentiment analysis:
 \begin{enumerate}
-\item \textbf{Naive Bayes} is a fair simple classifier that operates under the assumption that the presents or absence of features does not relate to the presents of other features.
-If we apply that on Twitter we would get $c = \arg\max_{c\in C} P(c|w)$ where $c$ is a sentiment class, $C$ the collection of sentiment classes and $w$ is a tweet.
+\item \textbf{Naive Bayes} is a fair simple classifier that operates under the assumption that the presents or absence of features does not relate to the presents of any of the other features.
+Applying that on Twitter with sentiment analysis, gives us $c = \arg\max_{c\in C} P(c|w)$ where $c$ is a sentiment class, $C$ the collection of sentiment classes and $w$ is a tweet.
 \cite{sentAnalysis}
@@
 This can be a very useful asset to take into account when assigning a sentiment to a tweet.
-The emoticons can be considered unigrams feature for some classifier.
+The emoticons can be considered unigram features for some classifier.
 There they will be strong evidence for a certain sentiment.
@@
 Using sentiment analysis all this information will become available\cite{machineLearning}.
-\subsection{Metadata analysis (opt)}
 
 \section{Tweet stream analysis}
-\subsection{Statistics}
+What we have seen so far was the analysis on one tweet.
+This is all very interesting from a computer science point of view.
+All the different techniques to extract the meaning of a tweet in such a way that it is machine interpretable.
+However, the real knowledge is in the big data, not in a single tweet.
+Extracting that knowledge poses a whole new set of problems.
 
@@
 \subsubsection{User Models}
-Before it is possible to classify a user, it is useful to create a model of a user. In their paper Fabel et al compare the following three ways to model a user. \cite{usermodel}
+Before it is possible to classify a user, it is useful to create a model of a user. In their paper F. Abel et al compare the following three ways to model a user. \cite{usermodel}
 \begin{itemize}
@@
 A friend account of user $x$ is an account that is followed by user $x$.
+%TODO read this over, second sentence unclear
 \\\\
 \textbf{Tweeting Behavior}\\
-Tweeting behavior is a set of characteristics which shows us the way a users interacts with twitter.
-Things like the average number of messages, number of replies \& number of friends seems a good quantifier for classification.
+Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter.
+Things like the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
 According to \cite{usermachine} these features are useful but not really discriminative.
@@
 Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
-According to \cite{usermachine} 80\% of the users provide a location and 48\% of the users provide a short bio.
+According to \cite{usermachine} 80\% of the users provides a location and 48\% of the users provides a short bio.
 Furthermore \cite{usermachine} was able to extract a gender for 80\% of the users, but with a very low accuracy.
@@
 
-To achieve this a combination of (political) hashtags in combination with twitter activities is used.
+To achieve this (political) hashtags in combination with twitter activities is used.
 To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts.
@@
 
-All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique. A subset is used as a holdout set, and a vector
-gets created with random weights that sum to 1. The recommender then modifies the vector over the holdout set to train the algorithm until it reaches
-a stable point. The algorithm then restarts to avoid local minima.
+All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique.
+A subset is used as a holdout set, and a vector gets created with random weights that sum to 1.
+The recommender then modifies the vector over the holdout set to train the algorithm until it reaches a stable point.
+The algorithm then restarts to avoid local minima.
 
@@
 
-The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has
-been developed for the purpose of tag-based recommendation systems. The model can be adapted to compute recommendations from tags used by Twitter. 
+The Pair-Wise Interaction Tensor Factorisation is a state-of-the-art algorithm that has been developed for the purpose of tag-based recommendation systems.
+The model can be adapted to compute recommendations from tags used by Twitter.
 The adaptation involves changing the roles of resources and tags with respect to each other.
@@
 This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor.
-The tensor is not directly linked to the dataset, but rather implies a ranking. It is therefor only useful in the case of tag-based resource recommendation, 
-and not for resource recommendations with other requirements.
+The tensor is not directly linked to the dataset, but rather implies a ranking.
+It is therefor only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
 
@@
 Event identification is the problem of identifying events(e.g.
-concerts, festivals \& incidents) in a twitter-stream.
+concerts, festivals and incidents) in a twitter-stream.
 The events identified range from Worldwide to local events.
-Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers \& News Sites)
+Twitter-messages related to an event can be a useful source of information as they often spread news earlier than the 'old' media (e.g News Papers and News Sites).
 
 To identify an event using an algorithm, a definition of an event is needed.
-\cite{eventident} defines an event as: "a real world occurence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the
-occurrence and published during time $T_e$."
+\cite{eventident} defines an event as: "a real world occurrence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the occurrence and published during time $T_e$."
 
@@
 \textbf{Separation of Event and Non-event Content}\\
-Because not all tweets on twitter are event content, a seperation of Event and Non-event content is done prior of identifying events.
+Because not all tweets on twitter are event content, a separation of Event and Non-event content is done prior of identifying events.
 To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA).
@@
   \item Temporal: The characteristics of the volume over the time $T_e$ associated with an event. 
-  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
+  \item Social: The interactions between users(e.g. retweets, replies and mentions) during events could differ from other activities. 
   \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
@@
 \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
+%TODO source toevoegen!
 
-At first the data is enriched, Twitter exposes the data using different formats such as JSON \& XML.
-To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable.
+At first the data is enriched, Twitter exposes the data using different formats such as JSON and XML.
+To make this data more machine readable \cite{eventalign} enrich the data with semantics, after this process the data can then  be used as linked data which is more machine readable.
 The full enrichment process is described in section 2 of \cite{eventalign}.
@@
 The first technique used by \cite{eventalign} is Feature Extraction.
-Three featuresets are used:
+Three feature sets are used:
 \begin{itemize}

### 2014-03-11 authorinstr_2.tex
Auteurs in plaats van nummers.

@@
 \textbf{Interaction Profiles}\\
-Users interaction profiles is a profile created by \cite{pol} to capture interactions between users and other accounts.
-An interaction is a retweet or a reply.
-\cite{usermachine} also uses friend accounts as a measurement in interaction between users.
-A friend account of user $x$ is an account that is followed by user $x$.
+Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts.
+\cite{pol} An interaction is a retweet or a reply.
+Pennacchiotti \& Popescu also uses friend accounts as a measurement in interaction between users.
+\cite{usermachine}  A friend account of user $x$ is an account that is followed by user $x$.
 %TODO read this over, second sentence unclear
@@
 Things like the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
-According to \cite{usermachine} these features are useful but not really discriminative.
+According to Pennacchiotti \& Popescu these features are useful but not really discriminative.
+\cite{usermachine}
 \\\\
@@
 Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
-According to \cite{usermachine} 80\% of the users provides a location and 48\% of the users provides a short bio.
-Furthermore \cite{usermachine} was able to extract a gender for 80\% of the users, but with a very low accuracy.
-\cite{usermachine} also researched the profile picture/avatar of twitter users.
-They found out that these pictures can often be misleading as 20\% of the found profile pictures was not the owner but another person such as a celebrity.
+According to Pennacchiotti \& Popescu  80\% of the users provides a location and 48\% of the users provides a short bio.
+\cite{usermachine} Furthermore their were able to extract a gender for 80\% of the users, but with a very low accuracy.
+They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading.
+20\% of the found profile pictures was not the owner but another person such as a celebrity.
+\cite{usermachine}
 
@@
 During election time it can be useful to predict the political preferences of a user.
-In \cite{pol} a solution to this problem is presented.
+In Makazhanov \& Raﬁei's paper a solution to this problem is presented.
 As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
+\cite{pol}
 
 To achieve this (political) hashtags in combination with twitter activities is used.
-To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts.
+To know if a user mentions an account of an election candidate Makazhanov \& Raﬁei semi-automatically scraped a number of these accounts.
 Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.
+\cite{pol}
 
@@
 To identify an event using an algorithm, a definition of an event is needed.
-\cite{eventident} defines an event as: "a real world occurrence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the occurrence and published during time $T_e$."
+Becker et al.
+define an event as: "a real world occurrence $e$ with (1) an associated Time Period $T_e$ and (2) a time-ordered stream of Twitter messages $M_e$, of substantial volume, discussing the occurrence and published during time $T_e$." \cite{eventident}
 
@@
 Because not all tweets on twitter are event content, a separation of Event and Non-event content is done prior of identifying events.
-To achieve this separation, \cite{eventident} uses an incremental clustering algorithm(ICA).
+To achieve this separation, Becker et al.
+use an incremental clustering algorithm(ICA).
 ICA doesn't require an number of clusters before the execution of the algorithm.
 This is an useful feature in the constantly changing twitter-environment.
+\cite{eventident}
 
-After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
+After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by Becker et al. to identify an event cluster. \cite{eventident} 
 \begin{itemize}
@@
 The first classifier is trained using the "WEKA tookit"\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, in the second classifier the  Naive-Bayes technique is used.
-According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters.
+According to Becker et al.
+the first classifier outperforms the second classifier in the separation of event and non-event clusters.
+\cite{eventident}
 \\\\
 \textbf{Aligning Tweets with an Event} \\
-On average thousands of tweets are sent every minute using Twitter(bron) .
+On average thousands of tweets are sent every minute using Twitter(\footnote{https://blog.twitter.com/2013/new-tweets-per-second-record-and-how}) .
 One of the main challenges in Event Identification is the alignment of tweets with their respective event.
-\cite{eventalign} tries to create an automated mapping solution for this problem using semantics.
-%TODO source toevoegen!
+Rowe \& Stankovic try to create an automated mapping solution for this problem using semantics.
+\cite{eventalign}
 
 At first the data is enriched, Twitter exposes the data using different formats such as JSON and XML.
-To make this data more machine readable \cite{eventalign} enrich the data with semantics, after this process the data can then  be used as linked data which is more machine readable.
-The full enrichment process is described in section 2 of \cite{eventalign}.
+To make this data more machine readable then they enrich the data with semantics, after this process the data can then  be used as linked data which is more machine readable.
+The full enrichment process is described in section 2 of Rowe \& Stankovic paper.
+\cite{eventalign}
 
 %TODO misschien wat meer info over het semantic web toevoegen.
-After this process \cite{eventalign} uses multiple techniques to align a tweet with the respective event.
-The first technique used by \cite{eventalign} is Feature Extraction.
-Three feature sets are used:
+After this process  Rowe \& Stankovic \cite{eventalign} uses multiple techniques to align a tweet with the respective event.
+The first technique used by them is Feature Extraction.
+\cite{eventalign} Three feature sets are used:
 \begin{itemize}
@@
 \subsubsection{Usecase: Earthquake Detection}
-In \cite{earthq} a usecase for Event Identification is presented in the form of a earthquake detection system.
-\cite{earthq} considers twitter users as sensors.
+In Sakaki et al.
+their paper a usecase for Event Identification is presented in the form of a earthquake detection system.
+\cite{earthq} They consider twitter users as sensors.
 If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.
@@
 In this time period 10 earthquakes had occurred, all of these earthquakes were detected.
-Furthermore \cite{earthq}'s system detects an earthquake 10 minutes after happening and sends a message within a minute after detection.
-
+Furthermore Sakaki et al.
+their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection.
+\cite{earthq}
 \newpage

### 2014-03-11 authorinstr_2.tex
Revision

@@
 
-Microblogging has grown out to be one of the most interesting forms of social media.
-One of its most popular implementations has to be Twitter, where users can share short messages, called Tweets, with any other user.
+Microblogging has grown out to become one of the most interesting forms of social media.
+Its most popular implementation has to be Twitter, where users can share short messages, called Tweets, with any other user.
 The limitation of 140 characters per Tweet forces users to compress all their information into a small message, making them extra interesting to analyze.
@@
 In the following section, Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets.
-After that, two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information.
+After that,
+two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information.
 The first section will focus on single tweets, and the second section is focused on sets of multiple Tweets.
@@
 
-When Twitter was founded, the creators chose to adopt an API (Application Specific Interface) for third party developers. This has proven to be very
-beneficial to both Twitter's popularity and a lot of its users, including researchers.
+When Twitter was founded, the creators chose to adopt an API (Application Programming Interface) for third party developers. This has proven to be very
+beneficial to both Twitter's popularity and a lot of its users, including researchers. An overview of the API structure and some useful fields\cite{TwitterDev}:
 
-An overview of the API structure and some useful fields:
 \begin{enumerate}
@@
 They can be used in an application that is build to handle these labels.
-Therefore Abel et al.
-propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g.
-DBpedia \footnote{http://dbpedia.
+Therefore
+Abel et al. propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g. DBpedia \footnote{http://dbpedia.
 org/}) can now be leveraged to enrich the data.
@@
 which make them hold interesting information about both the tweet and the user that posted it. There are two dominant techniques that are currently being
-used by researchers to model the information of tagged based analysis, The Linear-Weighted Hybrid Model, and the Pair-wise Interaction Tensor Factorisation Model.
+used by researchers to model the information of tagged based analysis, The Linear-Weighted Hybrid Model, and the Pair-wise Interaction Tensor Factorisation Model\cite{TagBased}.
 
@@
 
-With 
-\begin{enumerate}
+Where 
+\begin{itemize}
  \item $U_k$ the user factorization
@@
  \item $M$ the personalized resource-ranking tensor
-\end{enumerate}
+\end{itemize}
 
@@
 
-$\phi (u, \{t\}, r) = \sum_{i=1}^k U_k\{u\}\{i\}R_k^U\{r\}\{i\} + T_k\{t\}\{i\}R_k^T\{r\}\{i\}$	
+$\phi (u, \{t\}, r) = \sum_{i=1}^k U_k[u][i]R_k^U[r][i] + T_k[t][i]R_k^T[r][i]$	
 \end{enumerate}

### 2014-03-18 authorinstr_2.tex
Todo dingen
eerste aanpassingen

@@
 
-\title{Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)}
+\title{Seminarium TI 3700\\ Data Analysis on Twitter(working title)}
 \author{A. Hambenne  \and
@@
 \cite{usermachine}  A friend account of user $x$ is an account that is followed by user $x$.
-%TODO read this over, second sentence unclear
 \\\\
@@
 
-After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by Becker et al. to identify an event cluster. \cite{eventident} 
+After the clustering a number of features is used to distinguish between event and non-event clusters. The following features can be used to identify an event cluster. \cite{eventident} 
 \begin{itemize}
@@
   \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
-  \item Twitter-centric: Some activities behave like an event but are Twitter-centric.(e.g. Tweets like 'Goodmorning!') These activities need to be filtered. 
+  \item Twitter-centric: Some activities behave like an event but are Twitter-centric.(e.g.
+Tweets like 'Goodmorning!') These activities need to be filtered because a classifier might identify it as an event.
 \end{itemize}
@@
 The first classifier is trained using the "WEKA tookit"\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, in the second classifier the  Naive-Bayes technique is used.
-According to Becker et al.
-the first classifier outperforms the second classifier in the separation of event and non-event clusters.
+The first classifier outperforms the second classifier in the separation of event and non-event clusters.
 \cite{eventident}
@@
 
-%TODO misschien wat meer info over het semantic web toevoegen.
-After this process  Rowe \& Stankovic \cite{eventalign} uses multiple techniques to align a tweet with the respective event.
+After this process multiple techniques are used to align a tweet with the respective event.
 The first technique used by them is Feature Extraction.
-\cite{eventalign} Three feature sets are used:
+\cite{eventalign} The following three featuresets are used:
 \begin{itemize}
-%TODO uitwerken
+
   \item Immediate Resource Leaves: Use only the URI which are most indicative of an event. This feature only uses literals and resources within the URI of an event. 

### 2014-03-18 authorinstr_2.tex
Groot deel van User classification aangepast, uitgebreid en herschreven.

@@
 \subsubsection{User Models}
-Before it is possible to classify a user, it is useful to create a model of a user. In their paper F. Abel et al compare the following three ways to model a user. \cite{usermodel}
+Before it is possible to classify a user, it is useful to create a model of a user. In their paper F. Abel et al compare the following three ways to model a user \cite{usermodel}:
 \begin{itemize}
@@
 Linguistics can say a lot about the interests of a user.
-To classify a user Prototipical Words(PW's) can be used.
+Furthermore it can be used to distinguish between different types of users.
+One way to classify a user using linguistics is done by using Prototipical Words(PW's).
 \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$.
-In a twitter-context also Prototipical Hashtags can be used.
+(e.g.
+younger people will probably use terms like "lol" and "yolo" more than older users).
+To define prototipical words for i classes the propability that a user of class $c_i$ will use word $w$ needs to be calculated.
+Given n classes and some seed users $S_i$ this probability is calculated using the following formula: $proto(w, c_i) = \frac{|w, S_i|}{\sum_{j=1}^n |w, S_j|}$.
+\cite{userclasst} In a Twitter-context Prototipical Hashtags can be used in the same way.
+
+Another way to classify users is by applying the Latent Dirichlet Allocation (LDA), the idea behind this model is that some class $c_0$ will probably talk more about subject $A$ than class $c_1$ %TODO Afmaken
 \\\\
@@
 \cite{pol} An interaction is a retweet or a reply.
-Pennacchiotti \& Popescu also uses friend accounts as a measurement in interaction between users.
-\cite{usermachine}  A friend account of user $x$ is an account that is followed by user $x$.
+It is also possible to use friend accounts as a measurement in interaction between users.
+A friend account of user $x$ is an account that is followed by user $y$.
+In the same way as prototypical words are calculated prototypical replies and retweets can be calculated to classify a user.
+(e.g.
+a democrat may tend to retweet a message from a democratic candidate) \cite{userclasst}
 \\\\  
@@
 Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter.
-Things like the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
+Features such as the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
 According to Pennacchiotti \& Popescu these features are useful but not really discriminative.
-\cite{usermachine}
+\cite{userclasst}
 \\\\
@@
 Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
-According to Pennacchiotti \& Popescu  80\% of the users provides a location and 48\% of the users provides a short bio.
-\cite{usermachine} Furthermore their were able to extract a gender for 80\% of the users, but with a very low accuracy.
+Research has shown that 80\% of the users provides a location and 48\% of the users provides a short bio.
+\cite{usermachine} It is was possible to extract a gender for 80\% of the users, but with a very low accuracy.
 They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading.
@@
 As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
+\cite{pol} To achieve this (political) hashtags in combination with twitter activities is used.
+To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall.
+This resulted in the collection of 181972 tweets about politics.\cite{pol}
+
+Before processing these tweets non-personal and spam accounts had to be filtered.
+Using multiple techniques spam was filtered, but after filtering only 0.3\% of the accounts were labeled as spam.
+After a manual check none of these accounts seemed to be a spammer.
+But after removing spam accounts there are still some Non-Personal(NP)-accounts(e.g Businesses, official entities and News Papers)  that should be removed before processing the data.
+This is mostly done by using the provided profile information and filtering on city names in the user names.
 \cite{pol}
 
-To achieve this (political) hashtags in combination with twitter activities is used.
-To know if a user mentions an account of an election candidate Makazhanov \& Raﬁei semi-automatically scraped a number of these accounts.
-Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered.
+After all the preprocessing a one vs all classifier is trained to classify the users.
+This classifier will recognize one political party vs all other political parties.
+The classifier will give a confidence score how likely the user will belong to a party.
+Then all these scores are compared and the user will probably prefer the party with the highest score.
 \cite{pol}
-
-To classify the users a one vs all classifier is trained. (Which will recorgnize one party vs all other parties.) After this all information is combined to predict a political party for each user. 
 \subsection{Tag based analysis}

### 2014-03-18 authorinstr_2.tex
Nog meer aanpassingen

@@
 \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.
+%TODO uitbreiden
 
@@
 \cite{userclasst} In a Twitter-context Prototipical Hashtags can be used in the same way.
-
-Another way to classify users is by applying the Latent Dirichlet Allocation (LDA), the idea behind this model is that some class $c_0$ will probably talk more about subject $A$ than class $c_1$ %TODO Afmaken
 \\\\
@@
 To make this data more machine readable then they enrich the data with semantics, after this process the data can then  be used as linked data which is more machine readable.
-The full enrichment process is described in section 2 of Rowe \& Stankovic paper.
-\cite{eventalign}
-
 After this process multiple techniques are used to align a tweet with the respective event.
@@
   \item 1-Step Resource Leaves: Use all literals and resources within 1 step from the URI of an event. 
-  \item DBPedia Concepts: Also uses all the concepts from DBPedia 
+  \item DBPedia Concepts: Also uses all the concepts from DBPedia, the machine readable version of Wikipedia.
 \end{itemize}
@@
 Furthermore all stopwords are removed and everything is normalized to lowercase.
-\cite{eventalign} Then a labeling function is used to label the event.
+\cite{eventalign}
+
+Then a labeling function is used to label the event, two types of labeling functions are tested.
+(1) Proximity-based Clustering (PbC) (2) Naive Bayes.
+PbC is an algorithm similar to K-means with k already known.
+The collection of tweets $X$ is observed and the class is returned for whicht the distance of between an event it's mean and the tweet vector is minimized.
+The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$.
+The Naive Bayes approach outperforms PbC for all feature sets.
+\cite{eventalign}
 \subsubsection{Usecase: Earthquake Detection}
@@
 Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users.
-
 With the above feature set as basis, a system that detects earthquakes using twitter was built.

### 2014-03-19 authorinstr_2.tex
Uitbreiding usermodel
Meer dingen aangepast

@@
 \subsubsection{User Models}
-Before it is possible to classify a user, it is useful to create a model of a user. In their paper F. Abel et al compare the following three ways to model a user \cite{usermodel}:
+Before it is possible to classify a user, it is useful to create a model of a user.
+A user model can vary in three ways.
+It can vary in the type of profile, the data sources used to enrich the profiles and some temporal constraints.
+A user profile can be represented by $P(u) = \{(c, w(u,c))| c \in C, u \in U\}$.
+In this formula $u$ is a user in the set of user $U$ and $c$ is a concept in the set of concepts $C$ is a concept In their paper F.
+Abel et al compare the following three ways to create a user Profile \cite{usermodel}:
 \begin{itemize}
@@
 \item Topic-based
-
 \end{itemize}
@@
 \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.
-%TODO uitbreiden
 
@@
 The tensor is not directly linked to the dataset, but rather implies a ranking.
-It is therefor only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
+It is therefore only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
 

### 2014-03-19 authorinstr_2.tex
Intro Update

@@
 
-Microblogging has grown out to become one of the most interesting forms of social media.
-Its most popular implementation has to be Twitter, where users can share short messages, called Tweets, with any other user.
-The limitation of 140 characters per Tweet forces users to compress all their information into a small message, making them extra interesting to analyze.
-These Tweets often contain information broadcasted by the user in the form of opinions, emotions, interests, etc.
-One of the biggest challenges is finding a way to extract the intended information from these Tweets.
-Once the information is extracted however, the possible applications are endless.
-This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics.
-In the following section, Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets.
-After that,
+Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
+where users can share short messages, called Tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
+interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
+information technology. One of the biggest challenges is finding a way to extract the intended information from these Tweets. 
+This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. We will build up from
+the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. In the following section, 
+Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, 
 two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information.

### 2014-03-19 authorinstr_2.tex
update

--- 2014-03-18 authorinstr_2.tex
@@
 This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets.
+We will start of by discussing Data enrichment.
+This part will elaborate on the different techniques to enrich tweets in order to be able to do better analysis on that tweet.
+After that we will discuss Semantic analysis.
+In this section an overview is given of different techniques to do a sentiment analysis and how data enrichment can be used to improve the performance.
 \subsection{Data enrichment}
 At the very basis of the analysis of a tweet is data enrichment.
-Because the length of a tweet is restricted to 140 characters, the users of Twitter use language in creative ways.
-This way of communicating makes it sometimes, even for humans, hard to understand what a tweet is about.
+Because the length of a tweet is limited to 140 characters, the users of Twitter use language in creative ways.
+These ways of communicating makes it sometimes, even for humans, hard to understand what a tweet is about.
 To get a better understanding of the meaning of a tweet, a context is needed.
-For humans this is done by linking the concepts from the tweet to earlier acquired knowledge.
+For humans a context is created by linking the concepts from the tweet to earlier acquired knowledge.
 The same thing can be done by computers.
@@
 \subsubsection{Concept extraction}
-In this case by concepts we mean named entities such as names of locations, people and organizations.
+In this paper when we say concepts we mean named entities such as names of locations, people and organizations.
 To recognize these entities multiple learning algorithms or even combinations of learning algorithms have been proposed.
-The most common are the statistical learning algorithms.
+Nowadays the most common are the statistical learning algorithms.
 Think of algorithms like Maximum Entropy Models, Hidden Markov Models or neural networks.
@@
 All of them in decreasing frequency of use.\cite{EntityRecognition} Florian et al.
-have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} After the entities have been found, labels are assigned to distinguish between a person, an organization or a location.
-These labels on its own are not worth a lot.
-They can be used in an application that is build to handle these labels.
-Therefore
-Abel et al. propose to use the RDF.\cite{AdaptiveSearch} By doing so sources from the Semantic Web (e.g. DBpedia \footnote{http://dbpedia.
-org/}) can now be leveraged to enrich the data.
-Another advantage of using RDF is that RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}.
-Because W3C recommends to use this model, most likely a lot of other sources also use this model.
+have shown that combining multiple classifiers can increase the performance, compared to the best performing classifier, by 17-21 \%.\cite{ClassifierCombination} To do this they set up a framework to compare the results of different (combined) classifiers.
+
+After the entities have been found, labels are assigned to distinguish between a person, an organization or a location.
+Custom labels are not worth a lot.
+They can be used in an application that is specially build to handle these labels.
+To deal with this problem Abel et al.
+propose to use the RDF (Resource Description Framework).\cite{AdaptiveSearch} By using RDF to represent the data, sources from the Semantic Web (e.g.
+DBpedia \footnote{http://dbpedia.
+org/}) can now be leveraged to enrich the data because RDF is a Semantic Web standard recommended by the W3C\footnote{http://www.w3.org/RDF/}.
+Because W3C recommends to use this model, most likely a lot of resources also use this model.
 This will give a much bigger knowledge base to enrich the data from.
@@
 Every company wants to know how their newly launched product is doing, film makes want to know what people think about their new movie and politicians want to know how they are doing for the next elections.
-Using sentiment analysis all this information will become available\cite{machineLearning}.
+Using sentiment analysis all this information will become available as Pang et al.
+\cite{machineLearning} have shown in their research.
+They tried to classify documents based on their sentiment.
+In their research they used movie reviews as documents.
+They found that a semantical classifier outperforms human classification but compared to topic-based classification, sentiment classification falls behind.
+So even though there are enough possible applications for sentiment analysis, there is still a lot of room for improvement in this field.
 

### 2014-03-21 authorinstr_2.tex
conclusion

@@
 \cite{earthq}
-\newpage
 
 \section{Conclusion}
+In this paper we have tried to give an overview of the studies that have been done on analysis on Twitter and the question that still play in this field of study.
+We started off by introducing the Twitter API.
+This is the most important way to get data from Twitter.
+Here we also introduced all the different concept that can be retrieved from Twitter.
 
+In the following section we went up one level of abstraction.
+Here we discussed the techniques of analysis on a single tweet.
+Starting with data enrichment.
+This is the field of study where we try to give data more (machine-interpretable) meaning.
+We found that concept extraction is at the very basis of any enrichment technique and it is used to improve the performance of other algorithms.
+Because it is such a common technique, web services are available that can do this task.
+Next up was sentiment analysis.
+This is the labeling of a document according to its sentiment.
+From our literature it got clear that the performance of sentiment classifiers, even enhanced with emoticons, falls behind compared to topic classifiers.
+
+The next section was again a higher level of abstraction.
+In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets.
+First up was the user modeling.
+The idea here is that we can use the tweets from a certain user to create a profile from that user.
 \newpage

### 2014-03-22 authorinstr_2.tex
Intro met conclusie

@@
 Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
-where users can share short messages, called Tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
+where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
 interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
-information technology. One of the biggest challenges is finding a way to extract the intended information from these Tweets. 
-This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. We will build up from
-the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. In the following section, 
-Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, 
-two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information.
-The first section will focus on single tweets, and the second section is focused on sets of multiple Tweets.
-Both of these sections will involve several usecases for certain techniques.
-
-%TODO: Add what the conclusion will say
+information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets. 
+This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
+We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
+In the first following section the Twitter API will be evaluated, which will show that the platform offers useful tools and commands to retrieve 
+specific datasets, or even a completely random sample stream of tweets. Once Twitter's API has been evaluated, a first series of techniques will be introduced
+that focus on the analysis of a single tweet. These techniques offer insight in how machines and algorithms are being used to infer meaning from a tweet.
+However, certain applications require the analysis of a set of tweets instead of just a single one. The final chapter is therefore dedicated to the explanation\
+of common techniques used to retrieve information from multiple tweets. The conclusion of this paper involves a quick summary of the techniques that
+have been reviewed throughout this paper.
 

### 2014-03-22 authorinstr_2.tex
Abstract

@@
 \begin{abstract}
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
-This is the abstract of my paper.
+Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
+The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
+extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
+covering the API and a series of common techniques. One of the key factors that contribute to succesful extraction is data enrichment, or somehow enhancing
+the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
+When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
+insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
+for a variety of applications to be created using this information.
 \end{abstract}

### 2014-03-23 authorinstr_2.tex
Hoofdlettergebruik tweet, twitter enzo aangepast
Hoofdlettergebruik tweet, twitter enzo aangepast nu wel

@@
 extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
-covering the API and a series of common techniques. One of the key factors that contribute to succesful extraction is data enrichment, or somehow enhancing
+covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
 the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
@@
 information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets.
+
 This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
@@
 
-When the above fields are combined, it is possible to create datasets of Tweets that fulfill a certain specification.
+When the above fields are combined, it is possible to create datasets of tweets that fulfill a certain specification.
 These sets can then be used to extract specific information.
@@
 \cite{usermachine} It is was possible to extract a gender for 80\% of the users, but with a very low accuracy.
-They also researched the profile picture/avatar of twitter users and found out that these pictures can often be misleading.
+They also researched the profile picture/avatar of Twitter users and found out that these pictures can often be misleading.
 20\% of the found profile pictures was not the owner but another person such as a celebrity.
@@
 As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
-\cite{pol} To achieve this (political) hashtags in combination with twitter activities is used.
+\cite{pol} To achieve this (political) hashtags in combination with Twitter activities is used.
 To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall.
@@
 Event identification is the problem of identifying events(e.g.
-concerts, festivals and incidents) in a twitter-stream.
+concerts, festivals and incidents) in a Twitter-stream.
 The events identified range from Worldwide to local events.
@@
 \textbf{Separation of Event and Non-event Content}\\
-Because not all tweets on twitter are event content, a separation of Event and Non-event content is done prior of identifying events.
+Because not all tweets on Twitter are event content, a separation of Event and Non-event content is done prior of identifying events.
 To achieve this separation, Becker et al.
@@
 ICA doesn't require an number of clusters before the execution of the algorithm.
-This is an useful feature in the constantly changing twitter-environment.
+This is an useful feature in the constantly changing Twitter-environment.
 \cite{eventident}
@@
 their paper a usecase for Event Identification is presented in the form of a earthquake detection system.
-\cite{earthq} They consider twitter users as sensors.
+\cite{earthq} They consider Twitter users as sensors.
 If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.
@@
 Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users.
-With the above feature set as basis, a system that detects earthquakes using twitter was built.
+With the above feature set as basis, a system that detects earthquakes using Twitter was built.
 After the system detects an earthquake an email to all users is sent.

### 2014-03-23 authorinstr_2.tex
Wat aanpassingen
Wat uitbreidingen en kleine andere tweaks

@@
 
-When the above fields are combined, it is possible to create datasets of tweets that fulfill a certain specification.
+When the above fields are combined, it is possible to create datasets of tweets that fulfil a certain specification.
 These sets can then be used to extract specific information.
-However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyze.
+However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyse.
 For this purpose, Twitter has a streaming function that third party developers can tap into to retrieve random tweets.
@@
 Content-based strategies rely on the idea of finding as much similarity as possible between the content of a tweet and the content of a news article.
-The most similar tweet-article pair is considered to be related and therefor they are linked.
+The most similar tweet-article pair is considered to be related and therefore they are linked.
 	\subitem \textbf{Bag of words}, in this method a tweet is represented as a vector of word frequencies.
@@
 This body of text can very well be a tweet, and that combined with the popularity of microblogging amongst internet users, makes Twitter a very interesting body of knowledge about the opinion of a large group of people.
-But in order to get to that knowledge the data has to be analyzed fist.
+But in order to get to that knowledge the data has to be analysed fist.
 The most important and most obvious issue is how to extract an opinion from a tweet. In the next part we will discuss a few ways to extract an opinion from a tweet.
 \subsubsection{Semantics }
-The most important way to extract a sentiment from a tweet is by analyzing its semantics.
+The most important way to extract a sentiment from a tweet is by analysing its semantics.
 After all, tweets are written text.
@@
 \item \textbf{Training:} Because of their clear evidence for a sentiment emoticons can also be used to build a training corpus for a supervised learning algorithm.
-Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labeled accordingly.\cite{moodLens}
+Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labelled accordingly.\cite{moodLens}
 \end{enumerate}
@@
 Extracting that knowledge poses a whole new set of problems.
+In this part we will elaborate on User Classification, Tag Based analysis and Event Identification
 
 \subsection{User Classification}
-User classification is the problem of classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
-In this chapter we will discuss User Models, some features used to classify users and some use-cases.
+User classification is the problem of the classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
+In the first part of this chapter we will discuss User Models, whereas in the second part we will discuss some features used to classify users.
+We will also discuss how well these features can be used to classify users.
+At the end of this a practical use for these techniques and features is shown.
 \subsubsection{User Models}
@@
 After all these approaches are used on the same dataset it appears that the variety of entity-based profiles was much higher than the hashtag based approach.
+The number of distinct profile facets was higher than 10 in 99\% of the entity base profiles.
+Furthermore Entity \& Topic-based profile tends to have a more explicit semantic.
 \cite{usermodel} Furthermore the hashtag-based approach fails to create a profile for 5.5\% of the users where the other approaches don't have this problem.
@@
 \subsubsection{Classification Features}
-To classify users a set of features is needed to distinguish between users. In this section we will present a list of frequently used features to classify users.  
+While classifying users people are trying to discriminate between users.
+To achieve this a number of featuresets is needed.
+In this section we will discuss some features, their accuracy and the way they can be used to discriminate.
 \\\\
@@
 Given n classes and some seed users $S_i$ this probability is calculated using the following formula: $proto(w, c_i) = \frac{|w, S_i|}{\sum_{j=1}^n |w, S_j|}$.
-\cite{userclasst} In a Twitter-context Prototipical Hashtags can be used in the same way.
+In a Twitter-context Prototipical Hashtags can be used in the same way which perform better to classify a user on Twitter than prototypical words.
+\cite{userclasst}
 \\\\
-\textbf{Interaction Profiles}\\
-Users interaction profiles is a profile created by Makazhanov \& Raﬁei to capture interactions between users and other accounts.
+\textbf{Interaction}\\
+Users interaction is used by Makazhanov \& Raﬁei to capture interactions between users and other accounts.
 \cite{pol} An interaction is a retweet or a reply.
@@
 a democrat may tend to retweet a message from a democratic candidate) \cite{userclasst}
+\\\\
+\textbf{Interaction Profiles}\\
+Interaction Profiles are used to capture class-specific topics.
+Makazhanov \& Raﬁei use the following definition to get party specific terms for each party in an election: Given a set $C$ of candidates, we associate with each candidate $c \in C$ a document $d_c$ is modelled as a bag of words.
+Let $D = \{d_c| c \in C\}$ and for each party $p \in P$, $D_p = \{d_c | c $ is a member of $p\}$ \cite{pol}.
+To generate a Language Model (LM) divergence between the LM probability of a term in a party and the LM probability of all parties is used.
+With these probabilities for each term an importance score $I(t,p)$ is calculated to define the importance of term $t$ for party $p$.
+The higher the score the more it deviates from the normal election-tweets.
+\cite{pol}.
+To build the interaction profiles the top 100 terms for each party are included in a bag of words.
 \\\\  
@@
 \textbf{Profile}\\
-Profile information can be helpful to classify a user, but it should be used with care due to the amount of fake, inconsistent or incorrect information.
+Profile information can be helpful to bootstrap the classification of a user, but it should be used with care due to the amount of inconsistent, incorrect and sometimes bogus information (e.g an non-existent hometown).
 Research has shown that 80\% of the users provides a location and 48\% of the users provides a short bio.
 \cite{usermachine} It is was possible to extract a gender for 80\% of the users, but with a very low accuracy.
-They also researched the profile picture/avatar of Twitter users and found out that these pictures can often be misleading.
-20\% of the found profile pictures was not the owner but another person such as a celebrity.
+Only in 0.1\% of the cases the researchers where able to extract an etnicity.
+The profile picture/avatar of Twitter users can be misleading in 20\% of the found profile pictures not the owner was in the picture was but another person such as a celebrity.
 \cite{usermachine}
@@
 \subsubsection{Event Identification Issues}
-In this section we will discuss several issues regarding Event Identification and the solutions associated with them.
+Event identification has two main problem. (1) separating the content and non-event content in the constantly changing 
+Twitter-environment (2) Aligning tweets about an event with their respective event. In this section we will discuss these two problems and present a solution for them.
 \\\\ 
@@
 
-Then a labeling function is used to label the event, two types of labeling functions are tested.
+Then a labelling function is used to label the event, two types of labelling functions are tested.
 (1) Proximity-based Clustering (PbC) (2) Naive Bayes.
 PbC is an algorithm similar to K-means with k already known.
-The collection of tweets $X$ is observed and the class is returned for whicht the distance of between an event it's mean and the tweet vector is minimized.
+The collection of tweets $X$ is observed and the class is returned for which the distance of between an event it's mean and the tweet vector is minimized.
 The Naive Bayes approach uses the formula $y = \arg\max_{y \in Y} P(y)\prod_i P(x_i, y)$ to assign the most probable class label $y \in Y$ to tweet $x$.
@@
 Next up was sentiment analysis.
-This is the labeling of a document according to its sentiment.
+This is the labelling of a document according to its sentiment.
 From our literature it got clear that the performance of sentiment classifiers, even enhanced with emoticons, falls behind compared to topic classifiers.
@@
 In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets.
-First up was the user modeling.
+First up was the user modelling.
 The idea here is that we can use the tweets from a certain user to create a profile from that user.
-\newpage
 

### 2014-03-23 authorinstr_2.tex
Much Event identification, such user classification, very conclusive. Wow

@@
 In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets.
-First up was the user modelling.
-The idea here is that we can use the tweets from a certain user to create a profile from that user.
+We discussed User Classification, which can be a useful feature to gather information about people, their opinions and hobbies.
+These techniques can be used for predicting things people like such as their political view.
+We discussed the concept of event identification which can be separated in two problems (1) Separating event and non-event content and (2) Aligning Tweets with an Event.
+We presented solutions for these problems and shown that event identification can be a useful technique in practice.
+(e.g.
+It can be used to detect Earthquakes)
 

### 2014-03-24 authorinstr_2.tex
wow
conclusion conclusion

@@
 In this section an overview is given of different techniques to do a sentiment analysis and how data enrichment can be used to improve the performance.
-\subsection{Data enrichment}
+\subsection{Data Enrichment}
 At the very basis of the analysis of a tweet is data enrichment.
@@
 Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
-\subsubsection{Concept extraction}
+\subsubsection{Concept Extraction}
 In this paper when we say concepts we mean named entities such as names of locations, people and organizations.
@@
 Not only does it return the entities, it will also return facts and events hidden in the text, which will make the result even more useful.
-\subsubsection{Context creation}
+\subsubsection{Context Creation}
 The problem of linking tweets to another source of information poses one the biggest issue in data enrichment.
@@
 \begin{enumerate}
-\item \textbf{URL-based strategy}\\
+\item \textbf{URL-based Strategy}\\
 This strategy is based upon the observation that many tweets contains URLs. Usually these URLs refer to news articles the tweets are closely related to. Two URL-based strategies are proposed
@@
 These tweets will also be considered linked to $a$.
-\item \textbf{Content-based strategy}\\
+\item \textbf{Content-based Strategy}\\
 Content-based strategies rely on the idea of finding as much similarity as possible between the content of a tweet and the content of a news article.
 The most similar tweet-article pair is considered to be related and therefore they are linked.
-	\subitem \textbf{Bag of words}, in this method a tweet is represented as a vector of word frequencies.
+	\subitem \textbf{Bag of Words}, in this method a tweet is represented as a vector of word frequencies.
 For a news article we can also create a vector the represent it.
@@
 
-\subsection{Sentiment analysis}
+\subsection{Sentiment Analysis}
 Sentiment analysis or opinion mining is, as the Financial Times defines it, "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
@@
 \cite{pol}
-\subsection{Tag based analysis}
+\subsection{Tag Based Analysis}
 
@@
 
-The next section was again a higher level of abstraction.
-In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream of tweets and what information can be extracted from a stream of tweets.
-We discussed User Classification, which can be a useful feature to gather information about people, their opinions and hobbies.
-These techniques can be used for predicting things people like such as their political view.
-We discussed the concept of event identification which can be separated in two problems (1) Separating event and non-event content and (2) Aligning Tweets with an Event.
+The next section was again a higher level of abstraction. In this chapter we did not consider the data hidden in a single tweet, the focus was on a stream 
+of tweets and what information can be extracted from a stream of tweets. We discussed User Classification, which can be a useful feature to gather information 
+about people, their opinions and hobbies. These techniques can be used for predicting things people like such as their political view. Tag-based analysis is
+a set of techniques that allow researchers to find patterns within a set of tweets, based on the tagged content they contain. The two most common models
+were reviewed, being the linear-weighted hybrid model, and the pairwise interaction tensor factorisation. We discussed the 
+concept of event identification which can be separated in two problems (1) Separating event and non-event content and (2) Aligning Tweets with an Event.
 We presented solutions for these problems and shown that event identification can be a useful technique in practice.
@@
 
+Looking back we see that Twitter is a very useful source of information.
+Therefore the necessary research has been done on this topic already.
+Despites these efforts there is still a lot of room for improvement and new research.
+\newpage
 \bibliographystyle{plain}

### 2014-03-26 authorinstr_2.tex
Titel en bibtex aangepast. Krijg alleen de publishers niet toegevoegd aan de citaties
Ok de technieken van user modelling wat meer aan elkaar gepraat en hier en daar wat aangepast

@@
 \usepackage{a4wide}
+
 \usepackage{cite}
@@
 
-\title{Seminarium TI 3700\\ Data Analysis on Twitter(working title)}
+\title{Seminarium TI 3700\\ Data Analysis on Twitter: An Overview}
 \author{A. Hambenne  \and
@@
 While classifying users people are trying to discriminate between users.
-To achieve this a number of featuresets is needed.
-In this section we will discuss some features, their accuracy and the way they can be used to discriminate.
-\\\\
-\textbf{Linguistics}\\
+But to discriminate between users it is useful to know where to discriminate on.
+What are the best ways to classify a user?
+A lot of research has been done on classification In this section we will discuss some features, their accuracy and the way they can be used to classify a user.
+
+Classifying users by the topic they talk about seems a natural idea.
 Linguistics can say a lot about the interests of a user.
-Furthermore it can be used to distinguish between different types of users.
-One way to classify a user using linguistics is done by using Prototipical Words(PW's).
+One way to classify a user using linguistics is done by using Prototypical Words(PW's).
 \cite{userclasst} PW's are words that are more used by users in class $A$ than users in class $B$.
@@
 younger people will probably use terms like "lol" and "yolo" more than older users).
-To define prototipical words for i classes the propability that a user of class $c_i$ will use word $w$ needs to be calculated.
+To define prototypical words for i classes the probability that a user of class $c_i$ will use word $w$ needs to be calculated.
 Given n classes and some seed users $S_i$ this probability is calculated using the following formula: $proto(w, c_i) = \frac{|w, S_i|}{\sum_{j=1}^n |w, S_j|}$.
-In a Twitter-context Prototipical Hashtags can be used in the same way which perform better to classify a user on Twitter than prototypical words.
-\cite{userclasst}
-\\\\
-\textbf{Interaction}\\
-Users interaction is used by Makazhanov \& Raﬁei to capture interactions between users and other accounts.
+In a Twitter-context Prototypical Hashtags can be used in the same way which perform better to classify a user on Twitter than prototypical words.
+
+Another way to classify a user can be the people they interact with.
+Users their interaction is used by Makazhanov \& Raﬁei to capture interactions between users and other accounts.
 \cite{pol} An interaction is a retweet or a reply.
@@
 a democrat may tend to retweet a message from a democratic candidate) \cite{userclasst}
-\\\\
-\textbf{Interaction Profiles}\\
+
+Maybe it could be an idea to classify people on the terms they use.
 Interaction Profiles are used to capture class-specific topics.
@@
 To build the interaction profiles the top 100 terms for each party are included in a bag of words.
-\\\\  
-\textbf{Tweeting Behavior}\\
-Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter.
-Features such as the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
-According to Pennacchiotti \& Popescu these features are useful but not really discriminative.
-\cite{userclasst}
-\\\\
-\textbf{Profile}\\
+
+In real life people are also classified on their hometown, their age and their gender.
+Can this be achieved on Twitter using the profile information.
 Profile information can be helpful to bootstrap the classification of a user, but it should be used with care due to the amount of inconsistent, incorrect and sometimes bogus information (e.g an non-existent hometown).
@@
 \cite{usermachine}
+
+A maybe strange, but useful way to classify users is their   Tweeting behavior is a set of characteristics which shows us the way a user interacts with Twitter.
+Features such as the average number of messages, the number of replies and the number of friends seems a good quantifier for classification.
+According to Pennacchiotti \& Popescu these features are useful but not really discriminative.
+\cite{userclasst}
 

### 2014-03-26 authorinstr_2.tex
Enkele TODOs toegevoegd, moet ik nog aanpassen

@@
 \begin{abstract}
+
+%TODO: Dieper ingaan op onderwerpen, 'abstract' is enkel van toepassing op de paper, niet de onderwerpen
+
 Twitter is a popular microblogging website that allows users to share 140 character messages (tweets) with the rest of the world.
@@
 \section{Introduction}
+
+%TODO: Duidelijk zeggen dat het om een survey gaat, en een duidelijke werkmethodiek introduceren
 
@@
 
-\section{Data}
+\section{Before we start: Retrieving the right data}
+
+%TODO: Duidelijk Scheiden van de rest van het onderzoek
 
@@
 The following of this paper describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information can be applied to.
+
+%TODO: Inhoud is goed, vorm moet gestroomlijnder doorheen hele paper. Ook moet alles vanuit onze method geschreven worden, niet vanuit de papers
 
@@
 
+%TODO: Opsomming + stap naar toekomstig onderzoek maken
+
 \section{Conclusion}

### 2014-03-26 authorinstr_2.tex
Chapter 2 finalized, review conform

@@
 
-%TODO: Duidelijk Scheiden van de rest van het onderzoek
+Before we can research anything, we need the appropriate data to base our analysis on. The Twitter API, short for Application Programming Interface, is an
+interaction tool created by Twitter itself. It allows anyone to interact with their database through a set of commands published on their developer domain \cite{TwitterDev}.
+Researchers can use the API to create structures that can fetch tweets that satisfy a certain specification of their interest by manipulating the fields that
+the API uses to identify tweets and their content. If their research demands a more random tweet approach, a sample stream of random tweets can also be 
+obtained through these commands. Any researcher that has the intention of interacting with Twitter's database should familiarise him or herself with the 
+commands and the naming of the attributes used by the API. Following are some examples of possible commands.
 
-\subsection{Twitter API}
-
-When Twitter was founded, the creators chose to adopt an API (Application Programming Interface) for third party developers. This has proven to be very
-beneficial to both Twitter's popularity and a lot of its users, including researchers. An overview of the API structure and some useful fields\cite{TwitterDev}:
-
-\begin{enumerate}
+\begin{itemize}
 \item \textbf{Tweets} The short messages consisting of 140 characters sent by users
-	\subitem \textbf{coordinates} Returns the longitude and latitude position from where a specified tweet has been sent
+	\subitem \textbf{coordinates} Returns the longitude and latitude from where a tweet has been sent
 	\subitem \textbf{entities} Returns the entities (url, hashtag, etc.) that are embedded into the tweet
@@
 	\subitem \textbf{place\_type} Returns the type of a place, for example ``city''
-\end{enumerate}
+\end{itemize}
 
-When the above fields are combined, it is possible to create datasets of tweets that fulfil a certain specification.
-These sets can then be used to extract specific information.
-However, defining your own dataset may introduce a certain bias, and sometimes you need a random sample of tweets to analyse.
-For this purpose, Twitter has a streaming function that third party developers can tap into to retrieve random tweets.
-Unfortunately, the Twitter stream can only retrieve tweets that are less than a few days old.
+Now that we know how and where we should get our data from, we can start to analyse their content. The following 2 sections will illustrate
+several different techniques that can extract useful information from these tweets. We distinguish the extraction of features from a single tweet,
+and the analysis of bigger sets of tweets.
 
-The following of this paper describes algorithms that dive into the big data of Twitter, how to extract useful information from the tweets, and what the information can be applied to.
+\section{Single tweet analysis}
 
@@
 
-\section{Single tweet analysis}
 In this section we will discuss the different types of analysis that can be done on one single tweet.

### 2014-03-26 paper_final.tex
Paper geforked wegens geen feedback voor aanpassingen, heet nu paper_final
Aanpassing indeling

--- 2014-03-26 authorinstr_2.tex
@@
 
-\section{Single tweet analysis}
+\section{Techniques to analyse tweets}
 
+%\large
+%\hspace{9mm}\textbf{The analysis of a single tweet} ~
+%\normalsize
+%\newline
 %TODO: Inhoud is goed, vorm moet gestroomlijnder doorheen hele paper. Ook moet alles vanuit onze method geschreven worden, niet vanuit de papers
+
+\section*{Analysing a single tweet}
 
@@
 Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
-\subsubsection{Concept Extraction}
+\subsubsection*{Concept Extraction}
 In this paper when we say concepts we mean named entities such as names of locations, people and organizations.
@@
 Not only does it return the entities, it will also return facts and events hidden in the text, which will make the result even more useful.
-\subsubsection{Context Creation}
+\subsubsection*{Context Creation}
 The problem of linking tweets to another source of information poses one the biggest issue in data enrichment.
@@
 The most important and most obvious issue is how to extract an opinion from a tweet. In the next part we will discuss a few ways to extract an opinion from a tweet.
-\subsubsection{Semantics }
+\subsubsection*{Semantics }
 The most important way to extract a sentiment from a tweet is by analysing its semantics.
@@
 
-\subsubsection{Emoticons}
+\subsubsection*{Emoticons}
 Other than semantical analysis we can also use other data from tweets.
@@
 We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
-\subsubsection{Usage}
+\subsubsection*{Usage}
 The possibilities of sentiment analysis are not too hard to imagine.
@@
 
-\section{Tweet stream analysis}
+\section*{Analysing a set of tweets}
 What we have seen so far was the analysis on one tweet.
@@
 At the end of this a practical use for these techniques and features is shown.
-\subsubsection{User Models}
+\subsubsection*{User Models}
 Before it is possible to classify a user, it is useful to create a model of a user.
@@
 
-\subsubsection{Classification Features}
+\subsubsection*{Classification Features}
 While classifying users people are trying to discriminate between users.
@@
 
-\subsubsection{Usecase: Predicting Political Preferences}
+\subsubsection*{Usecase: Predicting Political Preferences}
+
+%TODO: Add to new chapter
+
 During election time it can be useful to predict the political preferences of a user.
@@
 
-\subsubsection{Event Identification Issues}
+\subsubsection*{Event Identification Issues}
 Event identification has two main problem. (1) separating the content and non-event content in the constantly changing 
@@
 \cite{eventalign}
-\subsubsection{Usecase: Earthquake Detection}
+\subsubsection*{Usecase: Earthquake Detection}
+
+%TODO: Add to new chapter
+
 In Sakaki et al.
@@
 \cite{earthq}
+
+\section{Applications that use tweet analysing techniques}
 

### 2014-03-26 paper_final.tex
enumerate naar itemize

@@
 
-%\large
-%\hspace{9mm}\textbf{The analysis of a single tweet} ~
-%\normalsize
-%\newline
 %TODO: Inhoud is goed, vorm moet gestroomlijnder doorheen hele paper. Ook moet alles vanuit onze method geschreven worden, niet vanuit de papers
+
+The data that Twitter provides in the form of tweets can be separated into two distinct parts. There is data specified to a single tweet, 
+and data that can be taken from a set of tweets. Both forms of data have different qualities, different attributes, different applications, and therefore
+also a different set of techniques used to analyse them compared to each other. This section is separated into the same two forms, with each section
+highlighting their respecive most common techniques used in the field of social web data analytics.
 
@@
 
-In this section we will discuss the different types of analysis that can be done on one single tweet.
-This usually is also the basis for a analysis of a larger amount of tweets or even on a stream of tweets.
-We will start of by discussing Data enrichment.
-This part will elaborate on the different techniques to enrich tweets in order to be able to do better analysis on that tweet.
-After that we will discuss Semantic analysis.
-In this section an overview is given of different techniques to do a sentiment analysis and how data enrichment can be used to improve the performance.
+The analysis of one single tweet forms the basis for the analysis of a bigger set of tweets. A single tweet is slightly harder to analyse because it usually
+lacks a pattern or an expected value. The challenge of single tweet analysis lies in the difficulty of making machine driven interfaces understand human
+intention and interpretation. It therefore forms the key to the analysis of bigger datasets of tweets, which reflects in the fact that the techniques used 
+to extract information from a single tweet usually reappear in extraction models used for bigger sets of tweets. 
+We will highlight the two most common techniques used to analyse a single tweet, being Data Enrichment and Sentiment Analysis. Data Enrichment is the
+enhancement of certain tweets by adding related data to simplify their analysis. Sentiment Analysis is the extraction of the intended sentiment behind a tweet.
+
 \subsection{Data Enrichment}
-At the very basis of the analysis of a tweet is data enrichment.
-Because the length of a tweet is limited to 140 characters, the users of Twitter use language in creative ways.
-These ways of communicating makes it sometimes, even for humans, hard to understand what a tweet is about.
-To get a better understanding of the meaning of a tweet, a context is needed.
-For humans a context is created by linking the concepts from the tweet to earlier acquired knowledge.
-The same thing can be done by computers.
-Two stages can be defined in this process, first the extraction of the concepts from the tweet, after that a context can be created by linking the tweet to other sources.
+
+At the very basis of the analysis of a tweet is data enrichment. Because the length of a tweet is limited to 140 characters, 
+the users of Twitter use language in creative ways. These ways of communicating makes it sometimes, even for humans, hard to understand what a tweet is about. 
+To get a better understanding of the meaning of a tweet, a context is needed. For humans a context is created by linking the concepts from the tweet to 
+earlier acquired knowledge. The same thing can be done by computers. Two stages can be defined in this process, first the extraction of the concepts from 
+the tweet, after that a context can be created by linking the tweet to other sources.
+
 \subsubsection*{Concept Extraction}
@@
 propose two main linking strategies, divided into five methods total.
-\begin{enumerate}
+\begin{itemize}
 \item \textbf{URL-based Strategy}\\
@@
 It relies on the entities that are mentioned in the article to make a vector to represent the article.
-\end{enumerate}
+\end{itemize}
 Using these method a broader context can be created.
@@
 \cite{machineLearning} have done a study on three standard machine learning algorithms for sentiment analysis:
-\begin{enumerate}
+\begin{itemize}
 \item \textbf{Naive Bayes} is a fair simple classifier that operates under the assumption that the presents or absence of features does not relate to the presents of any of the other features.
@@
 Not only will it separate the training data, it will do so at the largest possible margin.
-\end{enumerate}
+\end{itemize}
 It turns out that over the whole the Support Vector Machine performs the best on the sentiment analysis\cite{machineLearning}. The differences, however, are not substantially large.
@@
 The information from the emoticons can be leveraged in two ways
-\begin{enumerate}
+\begin{itemize}
 \item \textbf{Labeling:} The emoticons can be used to assign a sentiment to a tweet.
@@
 Twitter can be queried for "positive" emoticons and "negative" emoticons and then, by assuming the emoticon reflects the sentiment of message, the tweet can be labelled accordingly.\cite{moodLens}
-\end{enumerate}
+\end{itemize}
 We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
@@
 
-\begin{enumerate}
-\item \textbf{Linear-Weighted Hybrid}\\
+\subsubsection*{Linear-Weighted Hybrid}
 
@@
 
-\item \textbf{Pair-Wise Interaction Tensor Factorization}
+\subsubsection*{Pair-Wise Interaction Tensor Factorization}
 
@@
 $\phi (u, \{t\}, r) = \sum_{i=1}^k U_k[u][i]R_k^U[r][i] + T_k[t][i]R_k^T[r][i]$
-\end{enumerate}
 

### 2014-03-26 paper_final.tex
usecase migratie

@@
 
-\subsubsection*{Usecase: Predicting Political Preferences}
-
-%TODO: Add to new chapter
-
-During election time it can be useful to predict the political preferences of a user.
-In Makazhanov \& Raﬁei's paper a solution to this problem is presented.
-As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.
-\cite{pol} To achieve this (political) hashtags in combination with Twitter activities is used.
-To know if a user mentions an account of an election candidate a number of these accounts are scraped semi-automaticall.
-This resulted in the collection of 181972 tweets about politics.\cite{pol}
-
-Before processing these tweets non-personal and spam accounts had to be filtered.
-Using multiple techniques spam was filtered, but after filtering only 0.3\% of the accounts were labeled as spam.
-After a manual check none of these accounts seemed to be a spammer.
-But after removing spam accounts there are still some Non-Personal(NP)-accounts(e.g Businesses, official entities and News Papers)  that should be removed before processing the data.
-This is mostly done by using the provided profile information and filtering on city names in the user names.
-\cite{pol}
-
-After all the preprocessing a one vs all classifier is trained to classify the users.
-This classifier will recognize one political party vs all other political parties.
-The classifier will give a confidence score how likely the user will belong to a party.
-Then all these scores are compared and the user will probably prefer the party with the highest score.
-\cite{pol}
 \subsection{Tag Based Analysis}
@@
 0 and 1. The sum of all weights $\alpha_i$ has to be 1.
-
 Therefore, the hybrid model is defined as the function $\varphi (u, q, r) = \sum\limits_{i = 1}^k \alpha_i \phi_i (u,q,r)$
-
 All weights $\alpha_i$ are then computed by applying a random-restart hill climbing technique.
@@
 The adaptation involves changing the roles of resources and tags with respect to each other.
-
 This model is restricted in a way because its output is a set of matrices that illustrates a special case of the Tucker decomposition of a tensor.
@@
 It is therefore only useful in the case of tag-based resource recommendation, and not for resource recommendations with other requirements.
-
 To build the model, the data has to be observed in the form $(u, r+, r-, t)$ where $(u, r+, t)$ and $(u, r-, t)$ is a triple respectively
@@
 of the specialised tensor factorization:
-
 $M = U_k R_k^U + T_k R_k^T$
-
 Where 
@@
 \end{itemize}
-
 The relevance score of a resource can now be calculated by:
-
 $\phi (u, \{t\}, r) = \sum_{i=1}^k U_k[u][i]R_k^U[r][i] + T_k[t][i]R_k^T[r][i]$
@@
 \cite{eventalign}
-\subsubsection*{Usecase: Earthquake Detection}
-
-%TODO: Add to new chapter
-
-In Sakaki et al.
-their paper a usecase for Event Identification is presented in the form of a earthquake detection system.
-\cite{earthq} They consider Twitter users as sensors.
-If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an earthquake is occurring.
-
-To distinguish between tweets about Earthquakes a number of features is used.
-(1) The number of words in a tweet (2) The words in a tweet (3) Word context features.
-Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users.
-With the above feature set as basis, a system that detects earthquakes using Twitter was built.
-After the system detects an earthquake an email to all users is sent.
-The system was used during 18.
-august - 2 September.
-In this time period 10 earthquakes had occurred, all of these earthquakes were detected.
-Furthermore Sakaki et al.
-their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection.
-\cite{earthq}
 
 \section{Applications that use tweet analysing techniques}
+
+\subsection*{Predicting Political Preferences using User Classification}
+
+During election time it can be useful to predict the political preferences of a user. In Makazhanov \& Raﬁei's paper a solution to this problem is presented. 
+As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets. \cite{pol} To achieve this 
+(political) hashtags in combination with Twitter activities is used. To know if a user mentions an account of an election candidate a number of these 
+accounts are scraped semi-automaticall. This resulted in the collection of 181972 tweets about politics.\cite{pol}
+Before processing these tweets non-personal and spam accounts had to be filtered. Using multiple techniques spam was filtered, but after filtering 
+only 0.3\% of the accounts were labeled as spam. After a manual check none of these accounts seemed to be a spammer. But after removing spam accounts 
+there are still some Non-Personal(NP)-accounts(e.g Businesses, official entities and News Papers)  that should be removed before processing the data. 
+This is mostly done by using the provided profile information and filtering on city names in the user names.  \cite{pol}
+After all the preprocessing a one vs all classifier is trained to classify the users. This classifier will recognize one political party vs all other 
+political parties. The classifier will give a confidence score how likely the user will belong to a party. Then all these scores are compared and the user 
+will probably prefer the party with the highest score.  \cite{pol}
+
+\subsection*{Earthquake Detection using Event Detection}
+
+In Sakaki et al. their paper a usecase for Event Identification is presented in the form of a earthquake detection system. \cite{earthq} They consider 
+Twitter users as sensors. If enough sensors are activated (Tweets sent by a user are classified as a tweet about an earthquake), it is likely that an 
+earthquake is occurring. 
+To distinguish between tweets about Earthquakes a number of features is used. (1) The number of words in a tweet (2) The words in a tweet (3) Word context 
+features. Feature (1) is a surprisingly good way to classify tweets about earthquakes, especially if it is used with a big amount of users. With the above 
+feature set as basis, a system that detects earthquakes using Twitter was built. After the system detects an earthquake an email to all users is sent. 
+The system was used during 18. august - 2 September. In this time period 10 earthquakes had occurred, all of these earthquakes were detected. Furthermore 
+Sakaki et al. their system detects an earthquake 10 minutes after happening and sends a message within a minute after detection. 
+\cite{earthq}
 

### 2014-03-26 paper_final.tex
usecase chapter volledig

@@
 \section*{Analysing a set of tweets}
-What we have seen so far was the analysis on one tweet.
-This is all very interesting from a computer science point of view.
-All the different techniques to extract the meaning of a tweet in such a way that it is machine interpretable.
-However, the real knowledge is in the big data, not in a single tweet.
-Extracting that knowledge poses a whole new set of problems.
-In this part we will elaborate on User Classification, Tag Based analysis and Event Identification
+
+Now that we understand how the data of tweets are enriched, and how their sentiment is deduced, we hold the building blocks to create techniques that are able
+to analyse bigger sets of data. The analysis of a set of tweets is the key to creating applications based on Twitter information, of which some examples
+will be introduced in the next chapter. There are three common techniques used within the field of social web data analytics, which are the User Classification,
+the Tag Based Analysis and the Event Identification. The User Classification technique focussen on classifying every single tweet into a proposed set of classes.
+The Tag Based Analysis tries to link users based on the content that they attach to their tweets. Content can be another user, a hashtag subject, an image, url, etc.
+Event Identification has the goal of identifying real world events based upon a set of tweets.
 
@@
 
+We have seen how researcher obtain tweets for data, and how useful information is extracted from them. This chapter focussen on the application of this information.
+Given are two real world use cases that show why it is useful to extract information from the social web. The first use case illustrates the classification
+of users in political views in order to make predictions about an outcome of an election. The second use case is about how Twitter can be used to detect
+earthquakes by recognizing earthquake-related tweets that happen in real time.
+
 \subsection*{Predicting Political Preferences using User Classification}

### 2014-03-26 paper_final.tex
Intro 2.0

@@
 
-Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
-where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
-interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
-information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets.
-
-This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
+In the age of smartphones and glorified self-interest certain platforms have grown out to become massive databases filled with human-produced information.
+A very popular way of communicating is microblogging, where you share real-time short messages with everyone on the Internet. Today, the most succesful
+microblogging platform is Twitter, where users share 140 character messages (tweets) with the rest of the world. These short 140 messages often contain 
+valuable information about the user, their interests, opinions, etc. This information can be very useful for a variety of applications, 
+making social web data analytics an important field within information technology. One of the biggest challenges is finding a way to extract the intended 
+information from these tweets. This paper is a survey dedicated to giving an overview of successful techniques and useful applications of these social 
+web data analytics. Our working method involved analysing the methods of how researchers do their research on Twitter data. The overall method that emerged 
+were three distinct steps. The first step is the selection of data, in this case tweets, which can be done by using Twitters API. The second step was the 
+extraction of meaningful information from this data. The extraction process showed two separate perspectives. The single tweet perspective, where you extract
+information from a single tweet and its attributes, and the perspective of a set of tweets in which we look for a pattern. Both perspectives are separately
+handled within this paper. The third and final step was the application of the extracted information, where entities were created that build upon extracted 
+information.
+This paper is written from the perspective of these three steps.
 We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them.

### 2014-03-26 paper_final.tex
Abstract 2.0

@@
 The analysis of such messages has become its own field within information technology, with a range of techniques that all share the same cause:
-extracting useful information from these messages. This paper serves as an introduction to the research that has been done analysing tweets from Twitter,
-covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is data enrichment, or somehow enhancing
-the intended information from a tweet. This can be done by several techniques, yet this paper's scope limits to concept analysis and sentiment analysis.
+extracting useful information from these messages. This paper serves as a survey to the research that has been done analysing tweets from Twitter,
+covering the API and a series of common techniques. One of the key factors that contribute to successful extraction is Data Enrichment, or the enhancement
+the intended information from a tweet. Another key factor is Sentiment Analysis, where an intended sentiment is recognized from the tweets.
 When a stream of tweets is available for analysis, other techniques such as user classification, tag-based analysis and event identification offer valuable
-insights into the behaviour of users on Twitter. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
+insights into the behaviour of users on Twitter. The User Classification technique tries to divide a set of tweets over a set of proposed classes. 
+The Tag Based Analysis uses the content in a tweet to link users with each other. It uses attachments such as hashtags, urls, images, other users, etc. to
+create relations within a set of tweets. The final technique is Event Detection, where real time tweets are analysed to recognize real world events that
+are happening at some given time. Before we conclude the techniques, we illustrate some useful applications that can be accomplished by applying the extracted
+information. All these techniques allow researchers to extract interesting information from Twitter activity, and allow
 for a variety of applications to be created using this information.
@@
 \section{Introduction}
-
-%TODO: Duidelijk zeggen dat het om een survey gaat, en een duidelijke werkmethodiek introduceren
 

### 2014-03-26 paper_final.tex
Lee Out verbeterd

@@
 \begin{abstract}
-
-%TODO: Dieper ingaan op onderwerpen, 'abstract' is enkel van toepassing op de paper, niet de onderwerpen
 
@@
 
-%TODO: Inhoud is goed, vorm moet gestroomlijnder doorheen hele paper. Ook moet alles vanuit onze method geschreven worden, niet vanuit de papers
-
 The data that Twitter provides in the form of tweets can be separated into two distinct parts. There is data specified to a single tweet, 
@@
 \subsubsection*{Concept Extraction}
+
 In this paper when we say concepts we mean named entities such as names of locations, people and organizations.
@@
 Not only does it return the entities, it will also return facts and events hidden in the text, which will make the result even more useful.
+
 \subsubsection*{Context Creation}
+
 The problem of linking tweets to another source of information poses one the biggest issue in data enrichment.
@@
 \subsection{Sentiment Analysis}
+
 Sentiment analysis or opinion mining is, as the Financial Times defines it, "a linguistic analysis technique where a body of text is examined to characterize the tonality of the document."\footnote{http://lexicon.ft.com/Term?term=sentiment-analysis} In other words, the goal of a sentiment analysis is to extract the writers opinion on some topic from a body of text.
@@
 The most important and most obvious issue is how to extract an opinion from a tweet. In the next part we will discuss a few ways to extract an opinion from a tweet.
-\subsubsection*{Semantics }
+
+\subsubsection*{Semantics}
+
 The most important way to extract a sentiment from a tweet is by analysing its semantics.
@@
 \subsubsection*{Emoticons}
+
 Other than semantical analysis we can also use other data from tweets.
@@
 We now see that emoticons can be used to extract a sentiment from a tweet. However, they are not sufficient to just use emoticons to label the tweets. Simply because not all tweets contain emoticons.
+
 \subsubsection*{Usage}
+
 The possibilities of sentiment analysis are not too hard to imagine.
@@
 \subsection{User Classification}
+
 User classification is the problem of the classification of users based on (1) their metadata such as age, location and job and (2) the tweets a user has posted.
@@
 At the end of this a practical use for these techniques and features is shown.
+
 \subsubsection*{User Models}
+
 Before it is possible to classify a user, it is useful to create a model of a user.
@@
 \subsubsection*{Classification Features}
+
 While classifying users people are trying to discriminate between users.
@@
 \subsubsection*{Event Identification Issues}
+
 Event identification has two main problem. (1) separating the content and non-event content in the constantly changing 
@@
 \section{Conclusion}
+
 In this paper we have tried to give an overview of the studies that have been done on analysis on Twitter and the question that still play in this field of study.

### 2014-03-26 paper_final.tex
future research

--- 2014-03-26 paper_final.tex
@@
 
-In the age of smartphones and glorified self-interest certain platforms have grown out to become massive databases filled with human-produced information.
-A very popular way of communicating is microblogging, where you share real-time short messages with everyone on the Internet. Today, the most succesful
-microblogging platform is Twitter, where users share 140 character messages (tweets) with the rest of the world. These short 140 messages often contain 
-valuable information about the user, their interests, opinions, etc. This information can be very useful for a variety of applications, 
-making social web data analytics an important field within information technology. One of the biggest challenges is finding a way to extract the intended 
-information from these tweets. This paper is a survey dedicated to giving an overview of successful techniques and useful applications of these social 
-web data analytics. Our working method involved analysing the methods of how researchers do their research on Twitter data. The overall method that emerged 
-were three distinct steps. The first step is the selection of data, in this case tweets, which can be done by using Twitters API. The second step was the 
-extraction of meaningful information from this data. The extraction process showed two separate perspectives. The single tweet perspective, where you extract
-information from a single tweet and its attributes, and the perspective of a set of tweets in which we look for a pattern. Both perspectives are separately
-handled within this paper. The third and final step was the application of the extracted information, where entities were created that build upon extracted 
-information.
-This paper is written from the perspective of these three steps.
+Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
+where users can share short messages, called tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
+interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
+information technology. One of the biggest challenges is finding a way to extract the intended information from these tweets.
+
+This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. 
 We will build up from the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. 
@@
 Next up was sentiment analysis.
-This is the labelling of a document according to its sentiment.
+This is the labeling of a document according to its sentiment.
 From our literature it got clear that the performance of sentiment classifiers, even enhanced with emoticons, falls behind compared to topic classifiers.
@@
 a set of techniques that allow researchers to find patterns within a set of tweets, based on the tagged content they contain. The two most common models
-were reviewed, being the linear-weighted hybrid model, and the pairwise interaction tensor factorisation. We discussed the 
+were reviewed, being the linear-weighted hybrid model, and the pairwise interaction tensor factorization. We discussed the 
 concept of event identification which can be separated in two problems (1) Separating event and non-event content and (2) Aligning Tweets with an Event.
-We presented solutions for these problems and shown that event identification can be a useful technique in practice.
+We presented solutions for these problems and we have shown that event identification can be a useful technique in practice.
 (e.g.
 It can be used to detect Earthquakes)
+
+It got clear that there is always room for improvement in the existing techniques.
+For example, as mentioned earlier, in sentiment classification, there is room for improvement since its performance falls behind those of subject classification.
+We suspect this might be a matter of figuring out what features to use.
+We expect an increased interested from companies for the results of their advertisement campaigns.
+This would pose an interesting field for future research.
 

### 2014-03-26 paper_final.tex
faainal

--- 2014-03-26 paper_final.tex
@@
 \textbf{Separation of Event and Non-event Content}\\
+
 Because not all tweets on Twitter are event content, a separation of Event and Non-event content is done prior of identifying events.
@@
 \textbf{Aligning Tweets with an Event} \\
+
 On average thousands of tweets are sent every minute using Twitter(\footnote{https://blog.twitter.com/2013/new-tweets-per-second-record-and-how}) .
